### 2019-04-06 Paper_markdown.Rmd
Preliminary text

---
title: "Paper_text_working_file"
author: "Addison"
date: "April 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

install.packages("tidyverse")

library(tidyverse)

#This was a paper completed for the course Water and Conflict.

#Introduction
      With the recent military actions in Ukraine, the Saudi-Iranian proxy war in Yemen, and the ongoing civil war in Syria, it is easy to lose sight of arguably the most likely trigger area for a major interstate conflict today between great two powers. The continued dispute over the control of the South China Sea has resulted in several close encounters between military forces belonging to the United States and the Peoples Republic of China. In October of 2018 a Chinese destroyer passed within a few dozen feet of an American warship and on numerous occasions aircraft from both sides have intercepted one another in areal maneuvers with potentially global implications. With the increasing tensions in the South China Sea as well as the buildup of Chinese military forces in the region, the United States is challenged to meet to these actions or risk losing influence in a region with some of the most heavily used trade routes in the world. In order to do this the U.S. must deploy military assets thousands of miles from the nearest American shoreline and support those assets with steady stream of logistical and specialized support. This type of forward support can be accomplished through the use of overseas military installations. In terms of the South China Sea, American military bases in Korea, Guam, and Japan allow for the rapid deployment and sustainability of a large military force. China, for its part, has begun to build naval installations on the artificial islands it has constructed in the disputed zone. This would allow them to forward deploy their forces, as well as claim some level of legitimacy in their overall claim. 
     Naval bases placed abroad provide a state with the ability to project offensive force much further than if they were to only rely on military installations in their own territory. States with regional or even global hegemonic aspirations must build military outposts and naval installations if they have any hope projecting their power and influence beyond their own region. While there have been several studies that have looked into the effect of naval capacity on conflict initiation, there is very little research on the impact of fixed naval installations. In this paper I will try and fill that gap by examining the relationship between the proximity of a hegemon’s naval installations to initiating states of a maritime claim and the militarization of that dispute. In doing so this paper also examines several of the other prominent explanations for maritime claim militarization including relative capabilities of the disputants, regime typology, and specific issues about the claim (Hensel et al. 2008; Daniels & Mitchell 2017). The statistical analysis demonstrates that in fact proximity to a hegemon’s naval base does not have an effect on the militarization of a dispute. Further, this paper finds additional support for explanations based on issue salience for dispute militarization. 
     The remainder of the paper is divided into three sections, first will be a review of the relevant literature on military installations and their effects on conflict behavior. From this literature a theory will be developed linking naval installation proximity to conflict initiation. The second section will present the methods and data used in the statistical analysis. The third section will conclude the paper with a discussion about the implications of the findings and opportunities for future research.

#Review of relevant literature
     More than seventy percent of the Earth’s surface is covered by water, so to be able to extend one’s influence and capabilities abroad, preeminence on the seas is a must-have. Today the issue of a maritime strategy has become even more important to the global strategy of a state. Globalization and technological advances along with vastly lower costs of sea transportation has resulted in an explosion in the importance and prevalence of international trade. Companies like Maersk shipping operate more than 550 cargo vessels and acquire as many as forty more every ear (Carmel 2008, 41). As a result, states must create a global maritime strategy which allows them to protect their interests abroad and ensure safe and productive commerce. For some states this means constructing their own blue water navy to allow them to project their power beyond the literal and coastal waters. Other states will attempt to form alliances with powerful naval states to gain access to their ports and the protection of their fleets. New types of threats as well as resurgent threats also impact the chosen strategy of a state. To address irregular threats, the U.S. has taken a combined approach in their maritime strategy by working with international partners as well as the private sector to reduce the threat of piracy and terrorism (Carmel 2008, 40-41).	
     The radical changes in the maritime threat environment has brought about new security demands such as cyber security, anti-piracy, and the increasing need to protect the ever-growing commercial shipping lanes which fuel the global economy. Changes in different authorities have also altered the way in which states conduct their maritime strategy. IGOs such as the UN and international laws such as the United Nations Convention on the Law of the Sea (UNCLOS), mean that naval theorists must think about different types of authority beyond that of their own government (Luke 2013, 11-12). The United States has largely adhered to a similar strategy for more than one hundred years. Sea power has played a significant role in U.S. global strategy, thanks in no small part to the father of American maritime strategy, Alfred Thayer Mahan (Baofu 2008, 63-64). However, new maritime strategy has changed the way the United States operates and addresses maritime concerns. While old doctrine focuses on the construction of large fleets of capital ships to dominate potential opponents, the new strategy places a greater emphasis on the prevention of wars in the first place. (Baofu 2008, 65-66).  
     The vast oceans have a unique stopping power, preventing some of the most powerful state from achieving their goals. (Mearsheimer 2001, 84). One way to overcome this stopping power is by establishing a military installation outside of the state’s borders. This would allow the hegemon to extend its naval reach and support its forces further than it would if it solely relied on deploying forces from its own soil. Seaports allow states to assemble and hold large military forces and to support those forces far from their homeport (Julien 1984, 103). States which have been traditionally seen as being hegemonic powers such as the United States, Great Britain, Spain, and the Netherlands each had enormous preponderance in naval capabilities. Great Britain for example in the late 1800s possessed roughly half of all shipping tonnage in the world, along with military ports in colonies worldwide. (Calder 2008, 7). The United States for its part currently maintain more aircraft carriers than any other state and has more blue water naval assets deployed at any given time than any other country. Even in the face of U.S. decline and rising regional powers, most states still look to the U.S. for protection of sea lanes and general maritime policing (Henry et al. 2012, 32). The U.S. is so important to international maritime security that if it were to reduce its role in ensuring that security, international commerce would be severely impacted (Lee 2017, 6). 
     States with powerful navies such as the United States and Great Britain in the past, will use their naval power to protect their interests. This includes preventing foreign powers from establishing what some refer to as “command of the sea” (Corbett 1984, 161-169). One of the seminal works on the importance of naval power comes from Alfred Mahan. Mahan (2004) argued that naval dominance was necessary for states to assume command of the seas, thereby ensuring the success of land operations, cutting off lines of communication and commerce to an enemy, and protecting one’s own commerce and interests. Naval forces positioned in strategic locations like Gibraltar or the Suez can allow states to set up blockades and chokepoints, denying an enemy access to the sea and cutting off commerce. (Crowl 1986, 452-455). 
     A military base positioned outside of one’s borders can offer a state multiple advantages. These bases allow the state to respond to threats without risking conflict within their own borders while also allowing for greater flexibility in strategic deterrence. They allow states to apply their capabilities at strategic strong points and to draw on the resources and assistance of their allies (Calder 2008, 7-33). Along with military benefits, these bass allow countries to ensure the safe flow of vital resources necessary for modern industry. American military bases in Africa for example allow for the United States to ensure the safe flow of goods and oil from the Middle East and Asia to the West. These resources were important enough to the United States that bases were constructed, and a task force dubbed the Rapid Deployment Force (RDF) was created to protect American oil interests (Mangi 1987, 100). Military bases in foreign lands also have a symbolic effect by demonstrating the resolve and capabilities of the state to both allies and rivals (Namkung & Lee 2012, 30)  
     Many U.S. bases overseas arose following the end of past wars and have remained open even in the absence of a clear military need. In fact, military bases are surprisingly resilient when the U.S. attempts to draw down its military presence or make fiscal cuts (Davis et all 2012, 29). The importance of naval bases as a way to project power has also been taken to heart by aspiring hegemons such as China. Through their “string of pearls” strategy, China has been establishing outposts and securing alliances in foreign countries as a means of spreading influence and extending their reach. These outposts serve to protect oil shipments to China as well as establish new shipping routes for Chinese goods (Crisher 2017, 2). The importance of naval bases cannot be understated. Not only do they provide the ability to project hard power beyond a state’s borders, but also their ability to influence the economy and politics of surrounding countries. To a hegemon seeking to maintain the status quo and prevent the rise of a potential challenger, their contribution is vital.

Militarization of Maritime Claims
     The causes of maritime claim are often tied to disagreements over the management over some high valued resource. Fishing stocks, shipping routes, and non-renewable resources are often the causes that lead states to claim areas which are beyond their usual zone of control. While maritime claim rarely escalate to all wars, state shave threatened or even carried out lower levels of conflict. Militarized interstate disputes (MIDs) occur when states either threaten or carryout some form of military action short of war (Singer 1987). States will threaten or actively deploy military forces in response to perceived threats should their interests be at risk. 
     Several explanations have been presented for why maritime claims result in militarized disputes. One common explanation is economic opportunity or the availability of a high value resource. Oil and natural gas in particular have been found to increase the risk of a claim dispute escalating into militarized conflict (Nyman E2015, 1-7). Highly salient issues such as territorial claims, claims over areas with valuable resources, and areas considered to be in a strategic location have also been found to increase the risk of a militarized dispute (Hensel et al. 2008, 139).
     Another explanation for escalation, particularly in terms of territorial claims, is the change in relative capabilities of the actors involved. Bell (2017) finds that an increase in relative capabilities by a state which does not currently control the claimed territory dramatically increases the risk for armed conflict. However, research into maritime issues specifically has found that states with relatively equal capabilities are the most likely to see conflict. Disputes in which one state is overwhelmingly more powerful than the other are more likely to end in a peaceful settlement (Nemeth et al. 2014, 724; Hensel et al. 2008, 127).
     Proximity as a determinant in international conflict has been studied as it relates to escalation of conflicts among contiguous states as well as long distant conflicts. As Mearsheimer identified, oceans have a stopping power for states, preventing them from extending their influence and power (Mearsheimer 2001, 84). Kenneth Boulding (1962) argued that the power of a state is reduced as it tries to operate further from home. With each additional unit of distance, the ability of the state to influence others decreased. However, the impact of distance can be mitigated in certain circumstances. New technologies cut down on the amount of time that it takes to traverse vast distances, lessoning their impact (Starr 2005, 392). Navies allow for states to overcome the obstacle of oceans and distance and influence or engage noncontiguous states (Crisher 2017, 2). A naval base positioned closer to a hostile actor should allow for even more rapid, effective, and sustained intervention. These installations act as extensions of the state allowing them to deploy greater forces further and faster than if they were to only be based in the state’s territory (Julien 1984, 103).

#Theory
The theoretical foundation for this paper lies with hegemonic stability theory. According to the theory, a single overwhelmingly dominant state is necessary for the creation and maintenance of an open and stable international structure. The hegemon will provide public goods in the form of order and security to the international system by providing benefits to those states which stay in line and punishing those states which seek to upset the status quo. The states which initiate the claims are by definition states which seek to upset the status quo by acquiring rights to certain area or by acquiring sovereignty over them outright. These revisionist states threaten the status quo and thus draw the attention of the hegemon. While the hegemon may not become militarily involved in every dispute or conflict that occurs, their overwhelming dominance and ability to do so, should they chose, will weigh on the decision making of the revisionist state. 
	Naval installations provide states with a base from which to launch offensive operations as well as supply forces already deployed. This can be particularly useful to a hegemon which is trying to maintain the status quo of the international system of which it sits as its de facto head. Militarized conflicts between smaller states may threaten to upset that status quo or give rise to a potential challenger, forcing the hegemon to respond by involving itself in the dispute and if needs be punish the belligerents. A hegemonic power is especially responsive to maritime issues as international trade and the ability to move forces across the oceans freely are of keen interest to a hegemonic power. Maritime claim which result in a military conflict are then likely to draw the hegemon into the dispute. This is evident by the fact that the United States has been involved in roughly a third of the MIDs resulting from disputed maritime claims in the Issue Correlates of War data.  
	As a result, knowing that the hegemon has an interest in preventing military conflict will affect the conflict behavior of other states in the system. This effect will be felt disproportionality by states which are closer to the United States than those which are further away. For example, Cuba is justifiably more sensitive to U.S. intervention than Madagascar since U.S. ships and aircraft launched from the United States can reach Cuba in a matter of hours, whereas a campaign to Madagascar could take days or weeks. This is where naval installations factor into the theory. A naval facility on the other side of the world can act as an extension of the United States, permitting it to deploy and support fleets and air wings as though they had been launched from its own soil. If a revisionist state believed that it would take time for the hegemon to respond, or that the distance across the seas would dissuade their involvement, then that revisionist state may be more inclined to try and coerce a more favorable settlement out of the other actor. However, having a hegemon’s naval installation in close proximity to that challenger will cause the same constraining effect as being in close proximity to the hegemon itself. As a result:

H1) The likelihood of a militarized interstate dispute will increase as the distance between the challenger state and the nearest US naval installation increases.

	The United States will likely not become militarily involved in every dispute or maritime claim that arises, though they will have a position preference based on their role as the hegemon. However, if that maritime claim were against a state with which the U.S. held an alliance, then the incentives for the U.S. to become involve would rise substantially. Threats or actions against members of the hegemon’s alliance structure may challenge the assumption that the U.S. can protect those states. Not becoming involved in claims or disputes which involve an ally may call into question the very credibility of the other alliances and their role as the hegemon. States will understand this when formulating their strategy for a claim, and will be less inclined to allow a claim against a U.S. ally escalate into a militarized dispute. And so:

H2) The likelihood of a maritime claim developing into a militarized dispute is reduced when the target of the claim holds an alliance with the hegemon.

#Research design
Testing these hypotheses presented unique data limitations which had to be overcome. First, there is no public database of U.S. naval installations which contains geospatial and time series data. This data had to be gathered and a new dataset created. The Issue Correlates of War project publishes numerous datasets which contained the majority of the remainder of the information needed. Information on alliance structures and regime type were gathered from the Correlates of War project and Polity IV project respectively. After creating this dataset I test my hypotheses using a logistic regression with four models and report as coefficients rather than log-odds ratios.

Dependent Variable
     The dependent variable for these models is whether a militarized interstate dispute (MID) had occurred between the dyad over that claim in a given year. A MID is a military action ranging from threats to conflict short of war, which is defined as conflict exceeding 1000 battle deaths (Maoz et al. 2018, 7-8) . The Issue Correlates of War project has compiled a dataset of territorial, river, and maritime claims for nearly 200 dyad years. These claims are the argument between two or more actors that they have the right to use or take ownership of a specific maritime space. For example, the contention by China that it has economic rights to the maritime area within their so called Nine-Dash line. This dataset includes indicators on whether the claim resulted in a MID. This paper is particularly interested in maritime claim, and so both territorial and river disputes were dropped from the data. After dropping the two other types of issue claims, there were a total number of 3,226 dyad-years in which a maritime claim had occurred. Looking only at maritime claims, there were 91 dyad-years in which a dispute saw the initiation of a militarized dispute over that claim. The data was reduced further by removing those dyads in which the United States was either the instigator or the target of the dispute. This removed roughly a third of the available dyad years as well as a third of the MIDs. Data limitations associated with the relative capabilities of some states as well as the level of democracy removed an additional 25 dyad-years. We are then left with a total of 2,109 dyad years from which to analyze the relationships. Of 2,109 dyad-years of maritime claims, 67 resulted in the initiation of a MID.

Independent variables
     The primary independent variable of interest in this study is the proximity of United States naval installation. This variable is measured in terms of miles from the capital city of the state which made the original challenge, thus starting the maritime claim, to the nearest American naval installation. The capital city of the challenger is selected as the second geospatial starting point because it is the revisionist challenger which has initiated the claim by claiming some area which they do not currently possess. This upsets the status quo which the hegemon is attempting to maintain. 
     A list of naval bases is made public by the Commander, Navy Installations Command (CNIC). This list includes all currently active naval installations both inside the United States as well as overseas. Creating this variable required the creation of a data set with the observations for each naval instillation for each year that it was open. The dataset includes an identifier variable for each installation as well as the installations name. The year that the installation opened is recorded as well as the year it closed. If the installation has not closed but is currently still open, then the end year set to 2018. The latitude and longitude of the installation are also recorded as decimal coordinates. In addition to naval ports, naval air stations were included in this dataset. Naval aviation has become a major component of a state’s naval capabilities, evident by the replacement of the battleship by the aircraft carrier as the fleet’s principle capital ship (Julian 1984, 130). After using a statistical package to calculate the distance between the capital cities of the challenger states to the nearest US naval installation, we are left with 2,109 observations for the analysis.

#(Insert summary statistics/frequency table)

To test the other hypotheses and control for other explanations of dispute militarization, eight additional independent variable were added to the models. First among these are the relative capabilities of the two actors in the dispute. Measuring the capabilities of a state has become an entire body of literature unto itself. What do we mean by capabilities? How do we measure them? Which of these material capabilities contributes the most to a state’s power? All of these questions have been presented by researchers, and for each proposed answer there are a dozen counterarguments. Organski (1968) went so far as to claim that it would be easier to list those countries which have power than it would be to operationalize the concept itself. This research utilizes arguable the most widely used measure for material capabilities, the composite index of national capabilities (CINC) produced by the Correlates of War Program. This data takes six measures of national capabilities, total population, urban population, iron and steel production, energy consumption, military personnel, and military expenditures, and aggregates them into a single score (Singer 1987). CINC is not without its flaws, particularly its propensity to inflate scores for countries with high populations e.g. China, India, and Indonesia. CINC scores have also been found to indicate power transitions which do not occur and does not demonstrate transitions which have occurred (Kadera & Sorokin, 2004). Despite these shortcomings, CINC scores continue to be the most widely used measure of national capabilities, in no small part due to the wide time frame it encompasses and ease of use. To get a measure of relative capabilities, I borrow the relative capabilities measure used in Hensel et al’s. (2008) paper. By taking the strongest member of the dyad and divided their CINC score by the combined CINC of the dyad, I am left with a variable measuring the proportion of material capabilities held by the stronger member of the dyad. A relative capabilities measure near 0.5 would represent a nearly equal balance of power while a score closer to 1 would indicate relative preponderance by one member of the dyad (Hensel et al. 2008, 131). 
	Arguably the most pervasive theory in international relations is the concept of the democratic peace. Put simply, dyads in which both states are democratic tend not to fight in military conflicts with one another. Some researchers argue that it stems from the potential political costs a leader may face from their people (Fearon 1994, 557). Others have argued that democratic states are not presented with the opportunity to fight with one another since democratic states commonly have the same foreign policy preferences (Gartzke 1998). To control for joint democracy, I will include a dichotomous variable that identifies if both states are considered democratic. Categorizing the regime of a state will be done using the Polity IV data produced by the Center for Systemic Peace. Again borrowing the coding used by Hensel et al. (2008), any state which is scored as a 6 or greater on its democracy score will be considered a democratic regime. 
	Research has found that conflict behavior and alliance structures tends to be linked (Leeds 2003, 436). In this research I look specifically at whether the target or challenger have an alliance to the United States. To control for a possible alliance with the United States, I used the Formal Alliance data published by the Correlates of War project. Two variables, one identifying an alliance between the challenger and the United States, and another identifying an alliance between the target and the U.S. are included in the models. Four additional variables are included which account for different issues associated the maritime claim itself. The ICOW data includes these variables to identify the different aspects of issue salience of the particular claim. Included in the models are indicators for whether the claim is over a strategic location, over areas with oil or gas resources, other valuable non-oil resources, and fisheries. 
	Two interaction terms are included in the final model. The first is an interaction between the distance to the nearest US naval base and whether the target of the maritime claim has an alliance with the United States. Having an alliance with the United States may provide more incentive to the U.S. to get involved if a militarized dispute were to occur. This in turn may provide incentive for the challenger state to avoid initiating a MID. If the United States had a naval base near the challenger, this may dramatically increase the deterrence effect of an alliance. An interaction for the distance to a base and whether or not the disputed territory is considered a strategic location is also included in the fourth model. As the hegemonic power, the United States is keenly interested in the protection of trade routes and the openness of strategic waterways. Should the claim cover one of these strategic locations the United States will be more sensitive to attempts to change the status quo in that area, and so the distance to the revisionist state, the challenger, may affect the likelihood of the militarization of that dispute. 
	A final variable identifying whether there had been at least one attempt at bilateral negotiations to reach a settlement to the claim in a given year is included into the model. This variable was included to account for the willingness of the two states to find a peaceful solution. If the two states are willing to attempt a bilateral negotiation to solve the issue, it may indicate that they are more interested in seeking a peaceful settlement to the dispute. If this is true then we should see this variable indicate a negative relationship with the chance of the onset of a MID.

#Results
#Insert table 1
The results of all four models are given in Table 1. The first model is a simple bivariate logistic regression meant to observe the effects of installation proximity on MIDs by itself.  In this first model the relationship between distance to the nearest U.S. naval base and MID initialization is not statistically significant (P > 0.804). The coefficient appears to indicate an extremely weak inverse relationship between distance to an American naval installation and the challenger. However, the result is not significant. 
	Model 2 examines the effects of all controls without inclusion of distance to an American naval installation. Areas where a state may gain strategic benefits from the control of the region are more likely to see a militarized dispute develop. The results show a positive and significant (P > 0.012) relationship between whether the claim area is of strategic significance and the likelihood of a claim developing into a dispute control over strategic locations such as the Suez and Panama canals, Straits of Gibraltar, and Straits of Malacca could allow a state to ensure that trade and shipping move freely across the seas. Similarly, control over strategic locations could allow a state to restrict such commerce and transit. The importance of strategic location is also demonstrated with the interaction term of strategic area and distance being positive and significant. If the area under a claim is of strategic value and the distance from the challenger in the claim to a U.S. naval installation increases, the likelihood that a militarized dispute will occur increases. Additionally, the results demonstrate that the presence of oil in the area under claim will increase the likelihood that a MID may be initiated.  
	Also demonstrated in Model 2 is the profound effect which the history of bilateral attempts has on the likelihood of a claim becoming a dispute. However, the result is counter intuitive. If there is at least one attempt at a bilateral settlement to the dispute in a given year, then the likelihood that the claim will become a military dispute will actually increase. The effect is almost as large as the affect that strategic location has on MID likelihood and is significant at the .05 level. This may be the result of a failure of the attempted negotiation to garner any favorable terms, resulting in at least one side determining that a more aggressive strategy could be more profitable. 
	Model 3 isolates the indicators for different forms of issue salience to observe their impact on conflict by themselves. Once again, the presence of oil resources and the classification of the disputed area as a strategic location are found to be statistically significant. However, in this model the presence of migratory fish stock in the claimed area also increases the likelihood of the claim resulting in a militarized dispute. 
	The final model includes the independent variable as well as all controls. Again, we see that strategic location and the presence of oil resources have a statistically significant impact on the onset of MIDs. Most interesting in this model is that the independent variable becomes significant at the 0.05 level. As the distance between the nearest U.S. naval base and the challenger in the maritime claim increases, the likelihood of the claim becoming a militarized dispute increases as well thus supporting my hypothesis. Migratory fish stocks, which had been shown to impact MID likelihood in model 3, are not significant in this model. However, the interaction between distance and strategic importance is significant, as is the effect of at least one settlement attempt.

#Conclusion
	This paper attempts to further our knowledge of the impact of naval capabilities on maritime claims by focusing on fixed naval installations of a hegemonic power. By examining geospatial data this paper has demonstrated that as the distance between a hegemon’s naval installations and the challenger in maritime claim increases, the chance that a MID may occur rises, albeit very slightly. Issue specific aspects of maritime claims, namely the presence of oil in the disputed territory or the fact the claimed area is considered a strategic location were found to be significant. Area claims which are considered to be in a strategic location tend to increase the likelihood that the dispute will result in a militarized conflict. The relative capabilities of the dyad are not significant in any model, contrary to the findings of other studies (Hensel et al. 2008, 136). The presence of fishing resources or other valuable non-oil resources were also not found to have a significant effect on dispute militarization. However, migrating fishing stocks were found to have an effect in one model. Additionally, if there has been at least one attempt to negotiate a settlement to the claim in a year, then the likelihood of a MID surprisingly increases.
	While the Issue Correlates of War data provides researchers with a plethora of benefits and opportunities, the data on maritime conflict is still incomplete. To date, only two regions of maritime claims have been included in the data. This means that the relationship between installation proximity and dispute militarization may yield wildly different results when additional regions are added to the existing data. There is also the opportunity to expand this research by examining the relationship in a two stage analysis, looking at onset of a maritime claim as well as the onset of a militarized dispute. It may turn out that states self-select themselves into the sample of potential MIDs by being willing to risk the MID to make the initial claim.

#Need to include bibliography

### 2019-04-27 Paper_markdown.Rmd
Data merged, generating control variables, preparing for statistical tests.

@@
 ```
+#Packages
 
@@
 
+library(plyr)
 library(tidyverse)
+library(haven)
 
-#This was a paper completed for the course Water and Conflict.
+#Data generation process
 
-#Introduction
-      With the recent military actions in Ukraine, the Saudi-Iranian proxy war in Yemen, and the ongoing civil war in Syria, it is easy to lose sight of arguably the most likely trigger area for a major interstate conflict today between great two powers.
-The continued dispute over the control of the South China Sea has resulted in several close encounters between military forces belonging to the United States and the Peoples Republic of China.
-In October of 2018 a Chinese destroyer passed within a few dozen feet of an American warship and on numerous occasions aircraft from both sides have intercepted one another in areal maneuvers with potentially global implications.
-With the increasing tensions in the South China Sea as well as the buildup of Chinese military forces in the region, the United States is challenged to meet to these actions or risk losing influence in a region with some of the most heavily used trade routes in the world.
-In order to do this the U.S.
-must deploy military assets thousands of miles from the nearest American shoreline and support those assets with steady stream of logistical and specialized support.
-This type of forward support can be accomplished through the use of overseas military installations.
-In terms of the South China Sea, American military bases in Korea, Guam, and Japan allow for the rapid deployment and sustainability of a large military force.
-China, for its part, has begun to build naval installations on the artificial islands it has constructed in the disputed zone.
-This would allow them to forward deploy their forces, as well as claim some level of legitimacy in their overall claim.
-     Naval bases placed abroad provide a state with the ability to project offensive force much further than if they were to only rely on military installations in their own territory.
-States with regional or even global hegemonic aspirations must build military outposts and naval installations if they have any hope projecting their power and influence beyond their own region.
-While there have been several studies that have looked into the effect of naval capacity on conflict initiation, there is very little research on the impact of fixed naval installations.
-In this paper I will try and fill that gap by examining the relationship between the proximity of a hegemon’s naval installations to initiating states of a maritime claim and the militarization of that dispute.
-In doing so this paper also examines several of the other prominent explanations for maritime claim militarization including relative capabilities of the disputants, regime typology, and specific issues about the claim (Hensel et al.
-2008; Daniels & Mitchell 2017).
-The statistical analysis demonstrates that in fact proximity to a hegemon’s naval base does not have an effect on the militarization of a dispute.
-Further, this paper finds additional support for explanations based on issue salience for dispute militarization.
-     The remainder of the paper is divided into three sections, first will be a review of the relevant literature on military installations and their effects on conflict behavior.
-From this literature a theory will be developed linking naval installation proximity to conflict initiation.
-The second section will present the methods and data used in the statistical analysis.
-The third section will conclude the paper with a discussion about the implications of the findings and opportunities for future research.
+dyadic_mid_3_1_may_2018 <-as_tibble( read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/dyadic_mid_3.1_may_2018.dta"))
+View(dyadic_mid_3_1_may_2018)
 
-#Review of relevant literature
-     More than seventy percent of the Earth’s surface is covered by water, so to be able to extend one’s influence and capabilities abroad, preeminence on the seas is a must-have.
-Today the issue of a maritime strategy has become even more important to the global strategy of a state.
-Globalization and technological advances along with vastly lower costs of sea transportation has resulted in an explosion in the importance and prevalence of international trade.
-Companies like Maersk shipping operate more than 550 cargo vessels and acquire as many as forty more every ear (Carmel 2008, 41).
-As a result, states must create a global maritime strategy which allows them to protect their interests abroad and ensure safe and productive commerce.
-For some states this means constructing their own blue water navy to allow them to project their power beyond the literal and coastal waters.
-Other states will attempt to form alliances with powerful naval states to gain access to their ports and the protection of their fleets.
-New types of threats as well as resurgent threats also impact the chosen strategy of a state.
-To address irregular threats, the U.S.
-has taken a combined approach in their maritime strategy by working with international partners as well as the private sector to reduce the threat of piracy and terrorism (Carmel 2008, 40-41).
-     The radical changes in the maritime threat environment has brought about new security demands such as cyber security, anti-piracy, and the increasing need to protect the ever-growing commercial shipping lanes which fuel the global economy.
-Changes in different authorities have also altered the way in which states conduct their maritime strategy.
-IGOs such as the UN and international laws such as the United Nations Convention on the Law of the Sea (UNCLOS), mean that naval theorists must think about different types of authority beyond that of their own government (Luke 2013, 11-12).
-The United States has largely adhered to a similar strategy for more than one hundred years.
-Sea power has played a significant role in U.S.
-global strategy, thanks in no small part to the father of American maritime strategy, Alfred Thayer Mahan (Baofu 2008, 63-64).
-However, new maritime strategy has changed the way the United States operates and addresses maritime concerns.
-While old doctrine focuses on the construction of large fleets of capital ships to dominate potential opponents, the new strategy places a greater emphasis on the prevention of wars in the first place.
-(Baofu 2008, 65-66).
-     The vast oceans have a unique stopping power, preventing some of the most powerful state from achieving their goals.
-(Mearsheimer 2001, 84).
-One way to overcome this stopping power is by establishing a military installation outside of the state’s borders.
-This would allow the hegemon to extend its naval reach and support its forces further than it would if it solely relied on deploying forces from its own soil.
-Seaports allow states to assemble and hold large military forces and to support those forces far from their homeport (Julien 1984, 103).
-States which have been traditionally seen as being hegemonic powers such as the United States, Great Britain, Spain, and the Netherlands each had enormous preponderance in naval capabilities.
-Great Britain for example in the late 1800s possessed roughly half of all shipping tonnage in the world, along with military ports in colonies worldwide.
-(Calder 2008, 7).
-The United States for its part currently maintain more aircraft carriers than any other state and has more blue water naval assets deployed at any given time than any other country.
-Even in the face of U.S.
-decline and rising regional powers, most states still look to the U.S.
-for protection of sea lanes and general maritime policing (Henry et al.
-2012, 32).
-The U.S.
-is so important to international maritime security that if it were to reduce its role in ensuring that security, international commerce would be severely impacted (Lee 2017, 6).
-     States with powerful navies such as the United States and Great Britain in the past, will use their naval power to protect their interests.
-This includes preventing foreign powers from establishing what some refer to as “command of the sea” (Corbett 1984, 161-169).
-One of the seminal works on the importance of naval power comes from Alfred Mahan.
-Mahan (2004) argued that naval dominance was necessary for states to assume command of the seas, thereby ensuring the success of land operations, cutting off lines of communication and commerce to an enemy, and protecting one’s own commerce and interests.
-Naval forces positioned in strategic locations like Gibraltar or the Suez can allow states to set up blockades and chokepoints, denying an enemy access to the sea and cutting off commerce.
-(Crowl 1986, 452-455).
-     A military base positioned outside of one’s borders can offer a state multiple advantages.
-These bases allow the state to respond to threats without risking conflict within their own borders while also allowing for greater flexibility in strategic deterrence.
-They allow states to apply their capabilities at strategic strong points and to draw on the resources and assistance of their allies (Calder 2008, 7-33).
-Along with military benefits, these bass allow countries to ensure the safe flow of vital resources necessary for modern industry.
-American military bases in Africa for example allow for the United States to ensure the safe flow of goods and oil from the Middle East and Asia to the West.
-These resources were important enough to the United States that bases were constructed, and a task force dubbed the Rapid Deployment Force (RDF) was created to protect American oil interests (Mangi 1987, 100).
-Military bases in foreign lands also have a symbolic effect by demonstrating the resolve and capabilities of the state to both allies and rivals (Namkung & Lee 2012, 30)
-     Many U.S.
-bases overseas arose following the end of past wars and have remained open even in the absence of a clear military need.
-In fact, military bases are surprisingly resilient when the U.S.
-attempts to draw down its military presence or make fiscal cuts (Davis et all 2012, 29).
-The importance of naval bases as a way to project power has also been taken to heart by aspiring hegemons such as China.
-Through their “string of pearls” strategy, China has been establishing outposts and securing alliances in foreign countries as a means of spreading influence and extending their reach.
-These outposts serve to protect oil shipments to China as well as establish new shipping routes for Chinese goods (Crisher 2017, 2).
-The importance of naval bases cannot be understated.
-Not only do they provide the ability to project hard power beyond a state’s borders, but also their ability to influence the economy and politics of surrounding countries.
-To a hegemon seeking to maintain the status quo and prevent the rise of a potential challenger, their contribution is vital.
+#Renaming variables in MIDs data
+Dyadic_MID <- dyadic_mid_3_1_may_2018 %>%
+  rename(
+    ccodea = statea,
+    ccodeb = stateb
+  ) 
+Dyadic_MID
 
-Militarization of Maritime Claims
-     The causes of maritime claim are often tied to disagreements over the management over some high valued resource.
-Fishing stocks, shipping routes, and non-renewable resources are often the causes that lead states to claim areas which are beyond their usual zone of control.
-While maritime claim rarely escalate to all wars, state shave threatened or even carried out lower levels of conflict.
-Militarized interstate disputes (MIDs) occur when states either threaten or carryout some form of military action short of war (Singer 1987).
-States will threaten or actively deploy military forces in response to perceived threats should their interests be at risk.
-     Several explanations have been presented for why maritime claims result in militarized disputes.
-One common explanation is economic opportunity or the availability of a high value resource.
-Oil and natural gas in particular have been found to increase the risk of a claim dispute escalating into militarized conflict (Nyman E2015, 1-7).
-Highly salient issues such as territorial claims, claims over areas with valuable resources, and areas considered to be in a strategic location have also been found to increase the risk of a militarized dispute (Hensel et al.
-2008, 139).
-     Another explanation for escalation, particularly in terms of territorial claims, is the change in relative capabilities of the actors involved.
-Bell (2017) finds that an increase in relative capabilities by a state which does not currently control the claimed territory dramatically increases the risk for armed conflict.
-However, research into maritime issues specifically has found that states with relatively equal capabilities are the most likely to see conflict.
-Disputes in which one state is overwhelmingly more powerful than the other are more likely to end in a peaceful settlement (Nemeth et al.
-2014, 724; Hensel et al.
-2008, 127).
-     Proximity as a determinant in international conflict has been studied as it relates to escalation of conflicts among contiguous states as well as long distant conflicts.
-As Mearsheimer identified, oceans have a stopping power for states, preventing them from extending their influence and power (Mearsheimer 2001, 84).
-Kenneth Boulding (1962) argued that the power of a state is reduced as it tries to operate further from home.
-With each additional unit of distance, the ability of the state to influence others decreased.
-However, the impact of distance can be mitigated in certain circumstances.
-New technologies cut down on the amount of time that it takes to traverse vast distances, lessoning their impact (Starr 2005, 392).
-Navies allow for states to overcome the obstacle of oceans and distance and influence or engage noncontiguous states (Crisher 2017, 2).
-A naval base positioned closer to a hostile actor should allow for even more rapid, effective, and sustained intervention.
-These installations act as extensions of the state allowing them to deploy greater forces further and faster than if they were to only be based in the state’s territory (Julien 1984, 103).
+#Relative capabilities data
+NMC_5_0 <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/NMC_5_0.dta"))
+View(NMC_5_0)
+NMC <- select(NMC_5_0, ccode, year, irst, milex, milper, pec, tpop, upop, cinc)
+NMCA <- NMC %>%
+  rename(
+    ccodea = ccode,
+    irsta = irst,
+    milexa = milex,
+    milpera = milper,
+    peca = pec,
+    tpopa = tpop,
+    upopa = upop,
+    cinca = cinc
+  ) 
+NMCA
 
-#Theory
-The theoretical foundation for this paper lies with hegemonic stability theory.
-According to the theory, a single overwhelmingly dominant state is necessary for the creation and maintenance of an open and stable international structure.
-The hegemon will provide public goods in the form of order and security to the international system by providing benefits to those states which stay in line and punishing those states which seek to upset the status quo.
-The states which initiate the claims are by definition states which seek to upset the status quo by acquiring rights to certain area or by acquiring sovereignty over them outright.
-These revisionist states threaten the status quo and thus draw the attention of the hegemon.
-While the hegemon may not become militarily involved in every dispute or conflict that occurs, their overwhelming dominance and ability to do so, should they chose, will weigh on the decision making of the revisionist state.
-	Naval installations provide states with a base from which to launch offensive operations as well as supply forces already deployed.
-This can be particularly useful to a hegemon which is trying to maintain the status quo of the international system of which it sits as its de facto head.
-Militarized conflicts between smaller states may threaten to upset that status quo or give rise to a potential challenger, forcing the hegemon to respond by involving itself in the dispute and if needs be punish the belligerents.
-A hegemonic power is especially responsive to maritime issues as international trade and the ability to move forces across the oceans freely are of keen interest to a hegemonic power.
-Maritime claim which result in a military conflict are then likely to draw the hegemon into the dispute.
-This is evident by the fact that the United States has been involved in roughly a third of the MIDs resulting from disputed maritime claims in the Issue Correlates of War data.
-	As a result, knowing that the hegemon has an interest in preventing military conflict will affect the conflict behavior of other states in the system.
-This effect will be felt disproportionality by states which are closer to the United States than those which are further away.
-For example, Cuba is justifiably more sensitive to U.S.
-intervention than Madagascar since U.S.
-ships and aircraft launched from the United States can reach Cuba in a matter of hours, whereas a campaign to Madagascar could take days or weeks.
-This is where naval installations factor into the theory.
-A naval facility on the other side of the world can act as an extension of the United States, permitting it to deploy and support fleets and air wings as though they had been launched from its own soil.
-If a revisionist state believed that it would take time for the hegemon to respond, or that the distance across the seas would dissuade their involvement, then that revisionist state may be more inclined to try and coerce a more favorable settlement out of the other actor.
-However, having a hegemon’s naval installation in close proximity to that challenger will cause the same constraining effect as being in close proximity to the hegemon itself.
-As a result:
+NMCB <- NMC %>%
+  rename(
+    ccodeb = ccode,
+    irstb = irst,
+    milexb = milex,
+    milperb = milper,
+    pecb = pec,
+    tpopb = tpop,
+    upopb = upop,
+    cincb = cinc
+  ) 
+NMCB
 
-H1) The likelihood of a militarized interstate dispute will increase as the distance between the challenger state and the nearest US naval installation increases.
+#Importing naval data, removing all but the data for the U.S., keeping only relevant variables.
+crisher_souva_navaldata_II <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/crisher_souva_navaldata_II.dta"))
+View(crisher_souva_navaldata_II)
+Naval1 <- filter(crisher_souva_navaldata_II, cowcode == 2)
+Naval2 <- select(Naval1, year, totton, tonn_prop, milex, milper)
 
-	The United States will likely not become militarily involved in every dispute or maritime claim that arises, though they will have a position preference based on their role as the hegemon.
-However, if that maritime claim were against a state with which the U.S.
-held an alliance, then the incentives for the U.S.
-to become involve would rise substantially.
-Threats or actions against members of the hegemon’s alliance structure may challenge the assumption that the U.S.
-can protect those states.
-Not becoming involved in claims or disputes which involve an ally may call into question the very credibility of the other alliances and their role as the hegemon.
-States will understand this when formulating their strategy for a claim, and will be less inclined to allow a claim against a U.S.
-ally escalate into a militarized dispute.
-And so:
+#Importing PolityIV data and creating two seperate datasets to apply to both members of the dyad.
+PolityIV <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/PolityIV.dta"))
+view(PolityIV)
 
-H2) The likelihood of a maritime claim developing into a militarized dispute is reduced when the target of the claim holds an alliance with the hegemon.
+PolityIV1 <- select(PolityIV, year, ccode, democ, autoc, polity, polity2)
+PolityIVa <- PolityIV1 %>%
+  rename(
+    ccodea = ccode,
+    democa = democ,
+    autoca = autoc,
+    politya = polity,
+    polity2a = polity2
+  ) 
+view(PolityIVa)
 
-#Research design
-Testing these hypotheses presented unique data limitations which had to be overcome.
-First, there is no public database of U.S.
-naval installations which contains geospatial and time series data.
-This data had to be gathered and a new dataset created.
-The Issue Correlates of War project publishes numerous datasets which contained the majority of the remainder of the information needed.
-Information on alliance structures and regime type were gathered from the Correlates of War project and Polity IV project respectively.
-After creating this dataset I test my hypotheses using a logistic regression with four models and report as coefficients rather than log-odds ratios.
+PolityIVb <- PolityIV1 %>%
+  rename(
+    ccodeb = ccode,
+    democb = democ,
+    autocb = autoc,
+    polityb = polity,
+    polity2b = polity2
+  ) 
+PolityIVb
 
-Dependent Variable
-     The dependent variable for these models is whether a militarized interstate dispute (MID) had occurred between the dyad over that claim in a given year.
-A MID is a military action ranging from threats to conflict short of war, which is defined as conflict exceeding 1000 battle deaths (Maoz et al.
-2018, 7-8) .
-The Issue Correlates of War project has compiled a dataset of territorial, river, and maritime claims for nearly 200 dyad years.
-These claims are the argument between two or more actors that they have the right to use or take ownership of a specific maritime space.
-For example, the contention by China that it has economic rights to the maritime area within their so called Nine-Dash line.
-This dataset includes indicators on whether the claim resulted in a MID.
-This paper is particularly interested in maritime claim, and so both territorial and river disputes were dropped from the data.
-After dropping the two other types of issue claims, there were a total number of 3,226 dyad-years in which a maritime claim had occurred.
-Looking only at maritime claims, there were 91 dyad-years in which a dispute saw the initiation of a militarized dispute over that claim.
-The data was reduced further by removing those dyads in which the United States was either the instigator or the target of the dispute.
-This removed roughly a third of the available dyad years as well as a third of the MIDs.
-Data limitations associated with the relative capabilities of some states as well as the level of democracy removed an additional 25 dyad-years.
-We are then left with a total of 2,109 dyad years from which to analyze the relationships.
-Of 2,109 dyad-years of maritime claims, 67 resulted in the initiation of a MID.
+Atop <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/Atop_stata.dta"))
+view(Atop)
 
-Independent variables
-     The primary independent variable of interest in this study is the proximity of United States naval installation.
-This variable is measured in terms of miles from the capital city of the state which made the original challenge, thus starting the maritime claim, to the nearest American naval installation.
-The capital city of the challenger is selected as the second geospatial starting point because it is the revisionist challenger which has initiated the claim by claiming some area which they do not currently possess.
-This upsets the status quo which the hegemon is attempting to maintain.
-     A list of naval bases is made public by the Commander, Navy Installations Command (CNIC).
-This list includes all currently active naval installations both inside the United States as well as overseas.
-Creating this variable required the creation of a data set with the observations for each naval instillation for each year that it was open.
-The dataset includes an identifier variable for each installation as well as the installations name.
-The year that the installation opened is recorded as well as the year it closed.
-If the installation has not closed but is currently still open, then the end year set to 2018.
-The latitude and longitude of the installation are also recorded as decimal coordinates.
-In addition to naval ports, naval air stations were included in this dataset.
-Naval aviation has become a major component of a state’s naval capabilities, evident by the replacement of the battleship by the aircraft carrier as the fleet’s principle capital ship (Julian 1984, 130).
-After using a statistical package to calculate the distance between the capital cities of the challenger states to the nearest US naval installation, we are left with 2,109 observations for the analysis.
+politically_relevant <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/politically_relevant.dta"))
+view(politically_relevant)
 
-#(Insert summary statistics/frequency table)
+Master <- politically_relevant %>%
+  rename(
+    ccodea = ccode1,
+    ccodeb = ccode2, 
+  ) 
+Master
 
-To test the other hypotheses and control for other explanations of dispute militarization, eight additional independent variable were added to the models.
-First among these are the relative capabilities of the two actors in the dispute.
-Measuring the capabilities of a state has become an entire body of literature unto itself.
-What do we mean by capabilities?
-How do we measure them?
-Which of these material capabilities contributes the most to a state’s power?
-All of these questions have been presented by researchers, and for each proposed answer there are a dozen counterarguments.
-Organski (1968) went so far as to claim that it would be easier to list those countries which have power than it would be to operationalize the concept itself.
-This research utilizes arguable the most widely used measure for material capabilities, the composite index of national capabilities (CINC) produced by the Correlates of War Program.
-This data takes six measures of national capabilities, total population, urban population, iron and steel production, energy consumption, military personnel, and military expenditures, and aggregates them into a single score (Singer 1987).
-CINC is not without its flaws, particularly its propensity to inflate scores for countries with high populations e.g.
-China, India, and Indonesia.
-CINC scores have also been found to indicate power transitions which do not occur and does not demonstrate transitions which have occurred (Kadera & Sorokin, 2004).
-Despite these shortcomings, CINC scores continue to be the most widely used measure of national capabilities, in no small part due to the wide time frame it encompasses and ease of use.
-To get a measure of relative capabilities, I borrow the relative capabilities measure used in Hensel et al’s.
-(2008) paper.
-By taking the strongest member of the dyad and divided their CINC score by the combined CINC of the dyad, I am left with a variable measuring the proportion of material capabilities held by the stronger member of the dyad.
-A relative capabilities measure near 0.5 would represent a nearly equal balance of power while a score closer to 1 would indicate relative preponderance by one member of the dyad (Hensel et al.
-2008, 131).
-	Arguably the most pervasive theory in international relations is the concept of the democratic peace.
-Put simply, dyads in which both states are democratic tend not to fight in military conflicts with one another.
-Some researchers argue that it stems from the potential political costs a leader may face from their people (Fearon 1994, 557).
-Others have argued that democratic states are not presented with the opportunity to fight with one another since democratic states commonly have the same foreign policy preferences (Gartzke 1998).
-To control for joint democracy, I will include a dichotomous variable that identifies if both states are considered democratic.
-Categorizing the regime of a state will be done using the Polity IV data produced by the Center for Systemic Peace.
-Again borrowing the coding used by Hensel et al.
-(2008), any state which is scored as a 6 or greater on its democracy score will be considered a democratic regime.
-	Research has found that conflict behavior and alliance structures tends to be linked (Leeds 2003, 436).
-In this research I look specifically at whether the target or challenger have an alliance to the United States.
-To control for a possible alliance with the United States, I used the Formal Alliance data published by the Correlates of War project.
-Two variables, one identifying an alliance between the challenger and the United States, and another identifying an alliance between the target and the U.S.
-are included in the models.
-Four additional variables are included which account for different issues associated the maritime claim itself.
-The ICOW data includes these variables to identify the different aspects of issue salience of the particular claim.
-Included in the models are indicators for whether the claim is over a strategic location, over areas with oil or gas resources, other valuable non-oil resources, and fisheries.
-	Two interaction terms are included in the final model.
-The first is an interaction between the distance to the nearest US naval base and whether the target of the maritime claim has an alliance with the United States.
-Having an alliance with the United States may provide more incentive to the U.S.
-to get involved if a militarized dispute were to occur.
-This in turn may provide incentive for the challenger state to avoid initiating a MID.
-If the United States had a naval base near the challenger, this may dramatically increase the deterrence effect of an alliance.
-An interaction for the distance to a base and whether or not the disputed territory is considered a strategic location is also included in the fourth model.
-As the hegemonic power, the United States is keenly interested in the protection of trade routes and the openness of strategic waterways.
-Should the claim cover one of these strategic locations the United States will be more sensitive to attempts to change the status quo in that area, and so the distance to the revisionist state, the challenger, may affect the likelihood of the militarization of that dispute.
-	A final variable identifying whether there had been at least one attempt at bilateral negotiations to reach a settlement to the claim in a given year is included into the model.
-This variable was included to account for the willingness of the two states to find a peaceful solution.
-If the two states are willing to attempt a bilateral negotiation to solve the issue, it may indicate that they are more interested in seeking a peaceful settlement to the dispute.
-If this is true then we should see this variable indicate a negative relationship with the chance of the onset of a MID.
+#mergin in dyadic mid data
+Master2 <- full_join(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
 
-#Results
-#Insert table 1
-The results of all four models are given in Table 1.
-The first model is a simple bivariate logistic regression meant to observe the effects of installation proximity on MIDs by itself.
-In this first model the relationship between distance to the nearest U.S.
-naval base and MID initialization is not statistically significant (P > 0.804).
-The coefficient appears to indicate an extremely weak inverse relationship between distance to an American naval installation and the challenger.
-However, the result is not significant.
-	Model 2 examines the effects of all controls without inclusion of distance to an American naval installation.
-Areas where a state may gain strategic benefits from the control of the region are more likely to see a militarized dispute develop.
-The results show a positive and significant (P > 0.012) relationship between whether the claim area is of strategic significance and the likelihood of a claim developing into a dispute control over strategic locations such as the Suez and Panama canals, Straits of Gibraltar, and Straits of Malacca could allow a state to ensure that trade and shipping move freely across the seas.
-Similarly, control over strategic locations could allow a state to restrict such commerce and transit.
-The importance of strategic location is also demonstrated with the interaction term of strategic area and distance being positive and significant.
-If the area under a claim is of strategic value and the distance from the challenger in the claim to a U.S.
-naval installation increases, the likelihood that a militarized dispute will occur increases.
-Additionally, the results demonstrate that the presence of oil in the area under claim will increase the likelihood that a MID may be initiated.
-	Also demonstrated in Model 2 is the profound effect which the history of bilateral attempts has on the likelihood of a claim becoming a dispute.
-However, the result is counter intuitive.
-If there is at least one attempt at a bilateral settlement to the dispute in a given year, then the likelihood that the claim will become a military dispute will actually increase.
-The effect is almost as large as the affect that strategic location has on MID likelihood and is significant at the .05 level.
-This may be the result of a failure of the attempted negotiation to garner any favorable terms, resulting in at least one side determining that a more aggressive strategy could be more profitable.
-	Model 3 isolates the indicators for different forms of issue salience to observe their impact on conflict by themselves.
-Once again, the presence of oil resources and the classification of the disputed area as a strategic location are found to be statistically significant.
-However, in this model the presence of migratory fish stock in the claimed area also increases the likelihood of the claim resulting in a militarized dispute.
-	The final model includes the independent variable as well as all controls.
-Again, we see that strategic location and the presence of oil resources have a statistically significant impact on the onset of MIDs.
-Most interesting in this model is that the independent variable becomes significant at the 0.05 level.
-As the distance between the nearest U.S.
-naval base and the challenger in the maritime claim increases, the likelihood of the claim becoming a militarized dispute increases as well thus supporting my hypothesis.
-Migratory fish stocks, which had been shown to impact MID likelihood in model 3, are not significant in this model.
-However, the interaction between distance and strategic importance is significant, as is the effect of at least one settlement attempt.
+#Merging in polity iv datasets a and b.
+Master2 <- inner_join(Master2, PolityIVa, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- inner_join(Master2, PolityIVb, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
 
-#Conclusion
-	This paper attempts to further our knowledge of the impact of naval capabilities on maritime claims by focusing on fixed naval installations of a hegemonic power.
-By examining geospatial data this paper has demonstrated that as the distance between a hegemon’s naval installations and the challenger in maritime claim increases, the chance that a MID may occur rises, albeit very slightly.
-Issue specific aspects of maritime claims, namely the presence of oil in the disputed territory or the fact the claimed area is considered a strategic location were found to be significant.
-Area claims which are considered to be in a strategic location tend to increase the likelihood that the dispute will result in a militarized conflict.
-The relative capabilities of the dyad are not significant in any model, contrary to the findings of other studies (Hensel et al.
-2008, 136).
-The presence of fishing resources or other valuable non-oil resources were also not found to have a significant effect on dispute militarization.
-However, migrating fishing stocks were found to have an effect in one model.
-Additionally, if there has been at least one attempt to negotiate a settlement to the claim in a year, then the likelihood of a MID surprisingly increases.
-	While the Issue Correlates of War data provides researchers with a plethora of benefits and opportunities, the data on maritime conflict is still incomplete.
-To date, only two regions of maritime claims have been included in the data.
-This means that the relationship between installation proximity and dispute militarization may yield wildly different results when additional regions are added to the existing data.
-There is also the opportunity to expand this research by examining the relationship in a two stage analysis, looking at onset of a maritime claim as well as the onset of a militarized dispute.
-It may turn out that states self-select themselves into the sample of potential MIDs by being willing to risk the MID to make the initial claim.
+#merging in data on US naval capabilities
+Master2 <- inner_join(Master2, Naval2, by=c("year"), copy=FALSE, suffix=c("x", "y"))
 
-#Need to include bibliography
+#merging in data on material capabilities
+Master2 <- inner_join(Master2, NMCA, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- inner_join(Master2, NMCB, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+
+Master2 <- full_join(Master2, Atop, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+
+Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year <= 2012, year >= 1949)

### 2019-04-28 Paper_markdown.Rmd
Data generation and mutation complete

@@
 install.packages("tidyverse")
+install.packages("DataCombine")
 
@@
 library(tidyverse)
+library(DataCombine)
 library(haven)
@@
 Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year <= 2012, year >= 1949)
+
+#Creating a variable which only identifies if a mid occured in that dyad-year
+head(Master3$hihost, 1000)
+Master3 <- Master3 %>%
+    mutate(Mid = ifelse(is.na(hihost), 0, 1))
+head(Master3$Mid, 1000)
+
+#Creating a variable which only identifies if a Mid which involved the use of force occured in that dyad-year.
+head(Master3$hihost, 1000)
+Master3 <- Master3 %>%
+    mutate(Use_Force = ifelse(hihost > 3, 1, 0))
+Master3$Use_Force[is.na(Master3$Use_Force)] <- 0
+head(Master3$Use_Force, 1000)
+
+#Creating variable identifying joint democracy
+Master3 <- Master3 %>%
+    mutate(Joint_Dem = ifelse(politya >= 6 & polityb >=6, 1, 0))
+head(Master3$Joint_Dem, 1000)
+
+#Creating variable measuring relative capabilities
+Master3 <- filter(Master3, cinca != -9, cincb != -9)
+Master3 <- Master3 %>%
+    mutate(Relative_Cap = cinca/(cinca+cincb))
+head(Master3$Relative_Cap, 1000)
+
+#Creating variable identifying if at least one member of the dyad is a major power.
+Master3 <- Master3 %>%
+    mutate(Joint_Dem = ifelse(majpow1 == 1 | majpow2 == 1, 1, 0))
+head(Master3$Joint_Dem, 1000)
+
+#Creating a variable identifying if the dyad had experienced a MID in the previous two years.
+Master3 <- slide(Master3, Var = "Mid", GroupVar = "" slideBy = -2)
+
+#Variable identfying the presence of an alliance between the two members of the dyad
+Master3 <- Master3 %>%
+    mutate(Ally = ifelse(atopally ==1, 1, 0))
+Master3$Ally[is.na(Master3$Ally)] <- 0
+head(Master3$Ally, 1000)
+
+#Variable identifying if the two members of the dyad are in the same region
+Master3 <- Master3 %>%
+    mutate(Same_Region = ifelse(region1 == region2, 1, 0))
+head(Master3$Same_Region, 1000)
+
+#Creating a naval capability variable by modifying the systemic proportion of naval tonnage held by the US
+Master3 <- Master3 %>%
+    mutate(US_Naval_Cap =(milex/milper)*tonn_prop) 
+Master3 <- Master3 %>%
+    mutate(US_Naval_Cap = (US_Naval_Cap/10000)) 
+head(Master3$US_Naval_Cap, 1000)

### 2019-04-29 Paper_markdown.Rmd
Most statistical tests done. Need to create plots and double check against original STATA output.

@@
 install.packages("DataCombine")
+install.packages("dotwhisker")
 
@@
 library(haven)
+library(dotwhisker)
+
+options(digits = 4)
 
@@
 Master2 <- full_join(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+summary(Master2$year)
 
@@
 
-Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year <= 2012, year >= 1949)
+Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year < 2012, year >= 1950)
+
+#Variable Generation
 
@@
 Master3 <- Master3 %>%
-    mutate(Joint_Dem = ifelse(politya >= 6 & polityb >=6, 1, 0))
+    mutate(Joint_Dem = ifelse(polity2a >= 6 & polity2b >=6, 1, 0))
 head(Master3$Joint_Dem, 1000)
-
-#Creating variable measuring relative capabilities
-Master3 <- filter(Master3, cinca != -9, cincb != -9)
-Master3 <- Master3 %>%
-    mutate(Relative_Cap = cinca/(cinca+cincb))
-head(Master3$Relative_Cap, 1000)
 
@@
 Master3 <- Master3 %>%
-    mutate(Joint_Dem = ifelse(majpow1 == 1 | majpow2 == 1, 1, 0))
-head(Master3$Joint_Dem, 1000)
+    mutate(Major = ifelse(majpow1 == 1 | majpow2 == 1, 1, 0))
+head(Master3$Major, 1000)
 
@@
 head(Master3$US_Naval_Cap, 1000)
+
+#Binary variable identifying if the dyad year is during or after the Cold War
+Master3 <- Master3 %>%
+    mutate(Post_Cold_War = ifelse(year > 1990, 1, 0))
+
+#Creating variable measuring relative capabilities
+Master3 <- filter(Master3, cinca != -9, cincb != -9)
+Master3 <- Master3 %>%
+    mutate(Relative_Cap = cinca/(cinca+cincb))
+head(Master3$Relative_Cap, 1000)
+
+Master3 <- Master3 %>%
+    mutate(Hostility = 0) %>%
+    Hostility[hihost == 2] <- 1 %>%
+    Hostility[hihost == 3] <- 2 %>%
+    Hostility[hihost == 4] <- 3 %>%
+    Hostility[hihost == 5] <- 4 %>%
+    Hostility[ifelse(is.na(hihost))] <- 0
+
+Master3 <- Master3 %>%
+  rename(
+    Contiguous = contig,
+  )
+
+Master4 <- select(Master3, year, Mid, Use_Force, US_Naval_Cap, Same_Region, Contiguous, Ally, Joint_Dem, Relative_Cap, Major, Post_Cold_War)
+summary(Master4)
+
+#Statistical Tests
+
+#Bivariate Logits
+MID_BI_Log <- glm(Mid ~ US_Naval_Cap, data = Master4, family=binomial)
+summary(MID_BI_Log)
+dwplot(MID_BI_Log)
+
+Force_BI_Log <- glm(Use_Force ~ US_Naval_Cap, data = Master4, family=binomial)
+summary(Force_BI_Log)
+dwplot(Force_BI_Log)
+
+#Full Models
+  #Logistic regression
+MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Same_Region + Contiguous + Ally + Joint_Dem + Relative_Cap + Major + Post_Cold_War, data = Master4)
+summary(MID_Full_Log)
+dwplot(MID_Full_Log)
+
+Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Same_Region + Contiguous + Ally + Joint_Dem + Relative_Cap, data = Master4)
+summary(Force_Full_Log)
+dwplot(Force_Full_Log)
+
+  #Mlogit model
+Hostility_Mlog <- mlogit(Hostility ~ US_Naval_Cap + Same_Region + Contiguous + Ally + Joint_Dem + Relative_Cap, data = Master4, reflevel = 0)
+summary(Hostility_Mlog)
+dwplot(Hostility_Mlog)
+
+  #Heckman model

### 2019-05-01 Paper_markdown.Rmd
Needs to be cleaned up

--- 2019-04-27 Paper_markdown.Rmd
@@
 install.packages("tidyverse")
+install.packages("DataCombine")
+install.packages("dotwhisker")
+install.packages("data.table")
+install.packages("mlogit")
+install.packages("margins")
+install.packages("nnet")
+install.packages("reshape2")
 
@@
 library(tidyverse)
+library(DataCombine)
 library(haven)
+library(dotwhisker)
+library(data.table)
+library(mlogit)
+library(ggplot2)
+library(margins)
+library(nnet)
+library(reshape2)
 
 #Data generation process 
+#Prepping datasets for merging.
 
-dyadic_mid_3_1_may_2018 <-as_tibble( read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/dyadic_mid_3.1_may_2018.dta"))
+dyadic_mid_3_1_may_2018 <- as.data.frame( read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/dyadic_mid_3.1_may_2018.dta"))
 View(dyadic_mid_3_1_may_2018)
@@
   ) 
-Dyadic_MID
+Dyadic_MID <- select(Dyadic_MID, ccodea, ccodeb, year, hihost)
+view(Dyadic_MID)
 
 #Relative capabilities data
-NMC_5_0 <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/NMC_5_0.dta"))
+NMC_5_0 <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/NMC_5_0.dta"))
 View(NMC_5_0)
@@
 #Importing naval data, removing all but the data for the U.S., keeping only relevant variables.
-crisher_souva_navaldata_II <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/crisher_souva_navaldata_II.dta"))
-View(crisher_souva_navaldata_II)
+crisher_souva_navaldata_II <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/crisher_souva_navaldata_II.dta"))
 Naval1 <- filter(crisher_souva_navaldata_II, cowcode == 2)
 Naval2 <- select(Naval1, year, totton, tonn_prop, milex, milper)
+USNaval <- Naval2 %>%
+  rename(
+    ustoton = totton,
+    ustonn_prop = tonn_prop,
+    usmilex = milex,
+    usmilper = milper,
+  )  
+view(USNaval)
 
 #Importing PolityIV data and creating two seperate datasets to apply to both members of the dyad.
-PolityIV <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/PolityIV.dta"))
-view(PolityIV)
+PolityIV <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/PolityIV.dta"))
 
@@
     autoca = autoc,
-    politya = polity,
     polity2a = polity2
@@
     autocb = autoc,
-    polityb = polity,
     polity2b = polity2
@@
 
-Atop <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/Atop_stata.dta"))
-view(Atop)
+Alliance <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/alliance_v4.1_by_directed_yearly.dta"))
+Alliance <- Alliance %>%
+  rename(
+    ccodea = ccode1,
+    ccodeb = ccode2, 
+  )
 
-politically_relevant <- as_tibble(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/politically_relevant.dta"))
+Alliance <- select(Alliance, ccodea, ccodeb, year, defense, neutrality, nonaggression, entente)
+view(Alliance)
+
+politically_relevant <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/politically_relevant.dta"))
 view(politically_relevant)
@@
   ) 
-Master
+view(Master)
+
+#Merging datasets
 
@@
 Master2 <- full_join(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+summary(Master2)
+
+Master2 <- inner_join(Master2, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
 
@@
 Master2 <- inner_join(Master2, PolityIVb, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+summary(Master2)
 
 #merging in data on US naval capabilities
-Master2 <- inner_join(Master2, Naval2, by=c("year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- inner_join(Master2, USNaval, by=c("year"), copy=FALSE, suffix=c("x", "y"))
+
+plot(Naval2$year, Naval2$totton, main="US Naval Capabilities Over Time",
+    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Naval2$year,Naval2$totton), col="blue"))
 
@@
 
-Master2 <- full_join(Master2, Atop, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year < 2012, year >= 1950)
+summary(Master3)
 
-Master3 <- filter(Master2, ccodea != 2, ccodeb != 2, year <= 2012, year >= 1949)
+#Variable Generation
+
+#Creating a variable which only identifies if a mid occured in that dyad-year
+Master3 <- Master3 %>%
+    mutate(Mid = ifelse(is.na(hihost), 0, 1))
+summary(Master3$Mid)
+
+#Creating a variable which only identifies if a Mid which involved the use of force occured in that dyad-year.
+Master3 <- Master3 %>%
+    mutate(Use_Force = ifelse(hihost > 3, 1, 0))
+Master3$Use_Force[is.na(Master3$Use_Force)] <- 0
+summary(Use_Force)
+ftable(Use_Force)
+
+Master3$Hostility[is.na(Master3$hihost)] <- 0 
+Master3$Hostility[Master3$hihost==2] <- 1 
+Master3$Hostility[Master3$hihost==3] <- 2 
+Master3$Hostility[Master3$hihost==4] <- 3 
+Master3$Hostility[Master3$hihost==5] <- 4 
+ftable(Master3$Hostility)
+
+#Creating variable identifying joint democracy
+Master3 <- Master3 %>%
+    mutate(Joint_Dem = ifelse(polity2a >= 6 & polity2b >=6, 1, 0))
+head(Master3$Joint_Dem, 1000)
+
+#Creating variable measuring relative capabilities
+Master3 <- filter(Master3, cinca != -9, cincb != -9)
+Master3 <- Master3 %>%
+    mutate(Relative_Cap = cinca/(cinca+cincb))
+head(Master3$Relative_Cap, 1000)
+
+#Creating variable identifying if at least one member of the dyad is a major power.
+Master3 <- Master3 %>%
+    mutate(Major = ifelse(majpow1 == 1 | majpow2 == 1, 1, 0))
+head(Master3$Major, 1000)
+
+#Creating a variable identifying if the dyad had experienced a MID in the previous five years.
+Master3$Lag_Mid <- lag(Master3$Mid, 5)
+
+#Variable identfying the presence of an alliance between the two members of the dyad
+Master3 <- Master3 %>%
+    mutate(Ally = ifelse(atopally == "1", 1, 0))
+    mutate(Ally[is.na(Ally)] <- 0))
+    summary(Master3$atopally)
+summary(Master3$Ally)
+head(Master3$Ally, 1000)
+
+#Variable identifying if the two members of the dyad are in the same region
+Master3 <- Master3 %>%
+    mutate(Same_Region = ifelse(region1 == region2, 1, 0))
+head(Master3$Same_Region, 1000)
+
+#Creating a naval capability variable by modifying the systemic proportion of naval tonnage held by the US
+Master3 <- Master3 %>%
+    mutate(US_Naval_Cap =(usmilex/usmilper)*ustonn_prop) 
+Master3 <- Master3 %>%
+    mutate(US_Naval_Cap = (US_Naval_Cap/10000)) 
+head(Master3$US_Naval_Cap, 1000)
+
+plot(Master5$year, Master5$US_Naval_Cap, main="US Naval Capabilities Over Time",
+    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master5$year,Master5$US_Naval_Cap), col="blue"))
+
+#Binary variable identifying if the dyad year is during or after the Cold War
+Master3 <- Master3 %>%
+    mutate(Post_Cold_War = ifelse(year > 1990, 1, 0))
+
+Master3 <- Master3 %>%
+  rename(
+    Contiguous = contig,
+  )
+
+Master4 <- select(Master3, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid)
+summary(Master4)
+
+Master5 <- full_join(Master4, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+
+Master5 <- Master5 %>%
+    mutate(Ally =0)
+Master5$Ally[Master5$neutrality==1] <- 1 
+Master5$Ally[Master5$nonaggression==1] <- 1 
+Master5$Ally[Master5$defense==1] <- 1 
+Master5$Ally[Master5$entente==1] <- 1
+
+#Statistical Tests
+
+#Bivariate Logits
+MID_BI_Log <- glm(Mid ~ US_Naval_Cap, data = Master4, family=binomial)
+summary(MID_BI_Log)
+dwplot(MID_BI_Log)
+
+Force_BI_Log <- glm(Use_Force ~ US_Naval_Cap, data = Master4, family=binomial)
+summary(Force_BI_Log)
+dwplot(Force_BI_Log)
+
+#Full Models
+  #Logistic regression
+MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
+dwplot(MID_Full_Log)
+
+Master5 <- Master3 %>%
+    mutate(Relative_Cap = cinca/cincb)
+
+MID_Full_Log2 <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master5, family=binomial)
+summary(MID_Full_Log2)
+dwplot(MID_Full_Log2, show_intercept=TRUE, model_name = "Logistic Model", vline=geom_vline(xintercept=0), dot_args = list(size=3))
+exp(coef(MID_Full_Log2))
+
+margins(MID_Full_Log2)
+margins(MID_Full_Log2, at = list(US_Naval_Cap = 0:1))
+cplot(MID_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")
+
+Force_Full_Log2 <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master5, family=binomial)
+summary(Force_Full_Log2)
+dwplot(Force_Full_Log2, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
+exp(coef(Force_Full_Log2))
+test1 <- data.frame(exp(coef(Force_Full_Log2)))
+ggplot(exp(coef(Force_Full_Log2)))
+
+margins(Force_Full_Log2)
+cplot(Force_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of (violent)MID given US naval capabilities")
+
+MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War, data = Master4, family=binomial)
+summary(MID_Full_Log)
+dwplot(MID_Full_Log)
+
+Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
+summary(Force_Full_Log)
+dwplot(Force_Full_Log)
+
+  #Mlogit model
+Hostility_Mlog <- mlogit(Hostility ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Mlogit2, refleve=0)
+
+summary(Hostility_Mlog)
+dwplot(Hostility_Mlog)
+
+Master5 <- Master4
+Mlogit2 <- mlogit.data(Master5, varrying=7:14, choice="Hostility", shape="wide") 
+Mlogittest <- mlogit()
+
+Master6 <- Master5
+Master6$Hostility <- relevel(Master6$Hostility, ref = "0")
+test <- multinom(Hostility ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master6)
+summary(test)
+z <- summary(test)$coefficients/summary(test)$standard.errors
+p <- (1 - pnorm(abs(z), 0, 1)) *2
+
+exp(coef(test))
+head(pp <- fitted(test))
+test2 <- data.frame(Hostility = c("0", "1", "2", "3", "4"), US_Naval_Cap = mean(Master6$US_Naval_Cap), Relative_Cap = mean(Master6$Relative_Cap), Joint_Dem = mean(Master6$Joint_Dem), Major = mean(Master6$Major), Same_Region = mean(Master6$Same_Region), Contiguous = mean(Master6$Contiguous), Post_Cold_War = mean(Master6$Post_Cold_War), Lag_Mid = mean(Master6$Lag_Mid))
+predict(test, Master6 = test2, "probs")

### 2019-05-10 Paper_markdown.Rmd
Working

@@
 ---
-title: "Paper_text_working_file"
-author: "Addison"
-date: "April 5, 2019"
-output: html_document
+title: "Global Reach or Out of Reach"
+author: "Addison Huygens"
+date: "May 10, 2019"
+output:
+  pdf_document:
+    citation_package: natbib
+    fig_caption: yes
+    keep_tex: no
+    latex_engine: pdflatex
+    template: svm-latex-ms2.tex
+  word_document: default
+citecolor: black
+biblio-style: apsr
+endnote: no
+fontsize: 12pt
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
-```
-#Packages
-
 install.packages("tidyverse")
@@
 
+```
+#Packages
+
+```
 #Data generation process 
@@
 view(Master)
+```
 
+```
 #Merging datasets
@@
 
-Master2 <- inner_join(Master2, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- merge(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), all.x = TRUE, all.y = TRUE)
+
+Master2 <- left_join(Master2, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
 
 #Merging in polity iv datasets a and b.
-Master2 <- inner_join(Master2, PolityIVa, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
-Master2 <- inner_join(Master2, PolityIVb, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- left_join(Master2, PolityIVa, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- left_join(Master2, PolityIVb, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
 summary(Master2)
@@
 #merging in data on US naval capabilities
-Master2 <- inner_join(Master2, USNaval, by=c("year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- left_join(Master2, USNaval, by=c("year"), copy=FALSE, suffix=c("x", "y"))
 
@@
 #merging in data on material capabilities
-Master2 <- inner_join(Master2, NMCA, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
-Master2 <- inner_join(Master2, NMCB, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- left_join(Master2, NMCA, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- left_join(Master2, NMCB, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
 
@@
 summary(Master3)
+```
 
+```
 #Variable Generation
@@
 Master3 <- Master3 %>%
-    mutate(Relative_Cap = cinca/(cinca+cincb))
+    mutate(Relative_Cap = cinca/cincb)
 head(Master3$Relative_Cap, 1000)
@@
 
-Master4 <- select(Master3, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid)
+Master4 <- Master3 %>%
+    mutate(Ally =0)
+Master4$Ally[Master4$neutrality==1] <- 1 
+Master4$Ally[Master4$nonaggression==1] <- 1 
+Master4$Ally[Master4$defense==1] <- 1 
+Master4$Ally[Master4$entente==1] <- 1
+
+Master4 <- select(Master4, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid, Ally)
 summary(Master4)
+```
 
-Master5 <- full_join(Master4, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
-
-Master5 <- Master5 %>%
-    mutate(Ally =0)
-Master5$Ally[Master5$neutrality==1] <- 1 
-Master5$Ally[Master5$nonaggression==1] <- 1 
-Master5$Ally[Master5$defense==1] <- 1 
-Master5$Ally[Master5$entente==1] <- 1
-
+```
 #Statistical Tests
@@
   #Logistic regression
-MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
+MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally, data = Master4, family=binomial)
+summary(MID_Full_Log) 
 dwplot(MID_Full_Log)
@@
 predict(test, Master6 = test2, "probs")
+
+```
+
+This is a test

### 2019-05-10 Paper_markdown.Rmd
Still working

@@
     latex_engine: pdflatex
-    template: svm-latex-ms2.tex
+    template: svm-latex-ms2.tex.url
   word_document: default
@@
 
+options(tinytex.verbose = TRUE)
+
 ```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
-install.packages("tidyverse")
-install.packages("DataCombine")
-install.packages("dotwhisker")
-install.packages("data.table")
-install.packages("mlogit")
-install.packages("margins")
-install.packages("nnet")
-install.packages("reshape2")
+```
 
+```{r, include=FALSE}
 library(plyr)
@@
 
-```
+```{r, include=FALSE, cache=TRUE}
+options(tinytex.verbose = TRUE)
 #Data generation process 
@@
 view(Master)
+
 ```
 
-```
+```{r, include=FALSE, cache=TRUE}
+options(tinytex.verbose = TRUE)
 #Merging datasets
@@
 #mergin in dyadic mid data
-Master2 <- full_join(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
-summary(Master2)
-
 Master2 <- merge(Master, Dyadic_MID, by=c("ccodea", "ccodeb", "year"), all.x = TRUE, all.y = TRUE)
 
-Master2 <- left_join(Master2, Alliance, by=c("ccodea", "ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- merge(Master2, Alliance, by=c("ccodea", "ccodeb", "year"), all.x = TRUE)
 
 #Merging in polity iv datasets a and b.
-Master2 <- left_join(Master2, PolityIVa, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
-Master2 <- left_join(Master2, PolityIVb, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
-summary(Master2)
+
+Master2 <- merge(Master2, PolityIVa, by=c("ccodea", "year"), all.x = TRUE)
+
+Master2 <- merge(Master2, PolityIVb, by=c("ccodeb", "year"), all.x = TRUE)
 
 #merging in data on US naval capabilities
-Master2 <- left_join(Master2, USNaval, by=c("year"), copy=FALSE, suffix=c("x", "y"))
+
+Master2 <- merge(Master2, USNaval, by=c("year"), all.x = TRUE)
 
@@
 #merging in data on material capabilities
-Master2 <- left_join(Master2, NMCA, by=c("ccodea", "year"), copy=FALSE, suffix=c("x", "y"))
-Master2 <- left_join(Master2, NMCB, by=c("ccodeb", "year"), copy=FALSE, suffix=c("x", "y"))
+Master2 <- merge(Master2, NMCA, by=c("ccodea", "year"), all.x = TRUE)
+
+Master2 <- merge(Master2, NMCB, by=c("ccodeb", "year"), all.x = TRUE)
 
@@
 
-```
+```{r, include=FALSE, cache=TRUE}
+options(tinytex.verbose = TRUE)
 #Variable Generation
@@
 Master3$Use_Force[is.na(Master3$Use_Force)] <- 0
-summary(Use_Force)
-ftable(Use_Force)
+summary(Master3$Use_Force)
+ftable(Master3$Use_Force)
 
@@
 Master3 <- Master3 %>%
-    mutate(Ally = ifelse(atopally == "1", 1, 0))
-    mutate(Ally[is.na(Ally)] <- 0))
-    summary(Master3$atopally)
-summary(Master3$Ally)
-head(Master3$Ally, 1000)
+    mutate(Ally =0)
+Master3$Ally[Master3$neutrality==1] <- 1 
+Master3$Ally[Master3$nonaggression==1] <- 1 
+Master3$Ally[Master3$defense==1] <- 1 
+Master3$Ally[Master3$entente==1] <- 1
 
@@
 
-plot(Master5$year, Master5$US_Naval_Cap, main="US Naval Capabilities Over Time",
-    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master5$year,Master5$US_Naval_Cap), col="blue"))
+plot(Master3$year, Master3$US_Naval_Cap, main="US Naval Capabilities Over Time",
+    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master3$year,Master3$US_Naval_Cap), col="blue"))
 
@@
 
-Master4 <- Master3 %>%
-    mutate(Ally =0)
-Master4$Ally[Master4$neutrality==1] <- 1 
-Master4$Ally[Master4$nonaggression==1] <- 1 
-Master4$Ally[Master4$defense==1] <- 1 
-Master4$Ally[Master4$entente==1] <- 1
-
-Master4 <- select(Master4, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid, Ally)
+Master4 <- select(Master3, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid, Ally)
 summary(Master4)
@@
 
-```
+```{r, include=FALSE, cache=TRUE}
+options(tinytex.verbose = TRUE)
 #Statistical Tests
@@
 summary(MID_Full_Log)
-dwplot(MID_Full_Log)
 
-Master5 <- Master3 %>%
-    mutate(Relative_Cap = cinca/cincb)
+dwplot(MID_Full_Log, show_intercept=TRUE, model_name = "Logistic Model", vline=geom_vline(xintercept=0), dot_args = list(size=3))
+exp(coef(MID_Full_Log))
 
-MID_Full_Log2 <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master5, family=binomial)
-summary(MID_Full_Log2)
-dwplot(MID_Full_Log2, show_intercept=TRUE, model_name = "Logistic Model", vline=geom_vline(xintercept=0), dot_args = list(size=3))
-exp(coef(MID_Full_Log2))
-
-margins(MID_Full_Log2)
-margins(MID_Full_Log2, at = list(US_Naval_Cap = 0:1))
+margins(MID_Full_Log)
+margins(MID_Full_Log, at = list(US_Naval_Cap = 0:1))
 cplot(MID_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")
 
-Force_Full_Log2 <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master5, family=binomial)
+Force_Full_Log2 <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master4, family=binomial)
 summary(Force_Full_Log2)

### 2019-05-10 Paper_markdown.Rmd
Working on latex error

@@
 ---
-title: "Global Reach or Out of Reach"
-author: "Addison Huygens"
-date: "May 10, 2019"
 output: 
@@
     citation_package: natbib
-    fig_caption: yes
-    keep_tex: no
+    keep_tex: false
+    fig_caption: true
     latex_engine: pdflatex
     template: svm-latex-ms2.tex.url
-  word_document: default
+title: "Global Reach or Out of Reach"
+author: 
+- name: Addison Huygens
+  affiliation: University of Iowa
+abstract: "Here's where you write 100 to 250 words, depending on the journal, that describe your objective, methods, results, and conclusion."
+keywords: "Naval power hegemony"
+date: "May 10, 2019"
+fontsize: 12pt
+spacing: single
+bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "bib$"))`}
+biblio-style: apsr
 citecolor: black
-biblio-style: apsr
+linkcolor: black
 endnote: no
-fontsize: 12pt
 ---
 
-options(tinytex.verbose = TRUE)
+\begin{document}
+
+\begin{titlepage}
+
+test
+
+\end{titlepage}
 
@@
 knitr::opts_chunk$set(echo = TRUE)
-```
-
-```{r, include=FALSE}
 library(plyr)
@@
 ```
-#Packages
 
 ```{r, include=FALSE, cache=TRUE}
-options(tinytex.verbose = TRUE)
+
 #Data generation process 
@@
 ```{r, include=FALSE, cache=TRUE}
-options(tinytex.verbose = TRUE)
+
 #Merging datasets
@@
 ```{r, include=FALSE, cache=TRUE}
-options(tinytex.verbose = TRUE)
 #Variable Generation
@@
 Master3 <- Master3 %>%
-    mutate(Relative_Cap = cinca/cincb)
+    mutate(Relative_Cap = (cinca/cincb)/100000)
 head(Master3$Relative_Cap, 1000)
@@
   rename(
-    Contiguous = contig,
+    Contiguous = contig
   )
@@
 ```{r, include=FALSE, cache=TRUE}
-options(tinytex.verbose = TRUE)
+
 #Statistical Tests
@@
 summary(MID_BI_Log)
+ODDS_BI_MID <- exp(coef(MID_BI_Log))
 dwplot(MID_BI_Log)
@@
 summary(Force_BI_Log)
+ODDS_BI_FORCE <- exp(coef(Force_BI_Log))
 dwplot(Force_BI_Log)
-
-#Full Models
-  #Logistic regression
-MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally, data = Master4, family=binomial)
-summary(MID_Full_Log)
-
-dwplot(MID_Full_Log, show_intercept=TRUE, model_name = "Logistic Model", vline=geom_vline(xintercept=0), dot_args = list(size=3))
-exp(coef(MID_Full_Log))
-
-margins(MID_Full_Log)
-margins(MID_Full_Log, at = list(US_Naval_Cap = 0:1))
-cplot(MID_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")
-
-Force_Full_Log2 <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master4, family=binomial)
-summary(Force_Full_Log2)
-dwplot(Force_Full_Log2, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
-exp(coef(Force_Full_Log2))
-test1 <- data.frame(exp(coef(Force_Full_Log2)))
-ggplot(exp(coef(Force_Full_Log2)))
-
-margins(Force_Full_Log2)
-cplot(Force_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of (violent)MID given US naval capabilities")
-
-MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War, data = Master4, family=binomial)
-summary(MID_Full_Log)
-dwplot(MID_Full_Log)
-
-Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
-summary(Force_Full_Log)
-dwplot(Force_Full_Log)
-
-  #Mlogit model
-Hostility_Mlog <- mlogit(Hostility ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Mlogit2, refleve=0)
-
-summary(Hostility_Mlog)
-dwplot(Hostility_Mlog)
-
-Master5 <- Master4
-Mlogit2 <- mlogit.data(Master5, varrying=7:14, choice="Hostility", shape="wide") 
-Mlogittest <- mlogit()
-
-Master6 <- Master5
-Master6$Hostility <- relevel(Master6$Hostility, ref = "0")
-test <- multinom(Hostility ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master6)
-summary(test)
-z <- summary(test)$coefficients/summary(test)$standard.errors
-p <- (1 - pnorm(abs(z), 0, 1)) *2
-
-exp(coef(test))
-head(pp <- fitted(test))
-test2 <- data.frame(Hostility = c("0", "1", "2", "3", "4"), US_Naval_Cap = mean(Master6$US_Naval_Cap), Relative_Cap = mean(Master6$Relative_Cap), Joint_Dem = mean(Master6$Joint_Dem), Major = mean(Master6$Major), Same_Region = mean(Master6$Same_Region), Contiguous = mean(Master6$Contiguous), Post_Cold_War = mean(Master6$Post_Cold_War), Lag_Mid = mean(Master6$Lag_Mid))
-predict(test, Master6 = test2, "probs")
 
@@
 
-This is a test
+\end{document}

### 2019-05-10 Paper_markdown.Rmd
Test PDF produced

@@
     citation_package: natbib
-    keep_tex: false
+    keep_tex: true
     fig_caption: true
     latex_engine: pdflatex
-    template: svm-latex-ms2.tex.url
+    template: svm-latex-ms2.tex
 title: "Global Reach or Out of Reach"
@@
 
-\begin{document}
-
-\begin{titlepage}
-
-test
-
-\end{titlepage}
+Test
 
@@
 ```
-
-\end{document}

### 2019-05-11 Paper_markdown.Rmd

@@
 ---
-
-Test
 
@@
     mutate(Joint_Dem = ifelse(polity2a >= 6 & polity2b >=6, 1, 0))
-head(Master3$Joint_Dem, 1000)
 
@@
 Master3 <- Master3 %>%
-    mutate(Relative_Cap = (cinca/cincb)/100000)
-head(Master3$Relative_Cap, 1000)
+    mutate(Relative_Cap = cinca/cincb)
 
@@
     mutate(Major = ifelse(majpow1 == 1 | majpow2 == 1, 1, 0))
-head(Master3$Major, 1000)
 
@@
     mutate(Same_Region = ifelse(region1 == region2, 1, 0))
-head(Master3$Same_Region, 1000)
 
@@
     mutate(US_Naval_Cap = (US_Naval_Cap/10000))
-head(Master3$US_Naval_Cap, 1000)
 
-plot(Master3$year, Master3$US_Naval_Cap, main="US Naval Capabilities Over Time",
-    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master3$year,Master3$US_Naval_Cap), col="blue"))
+#Spending per soldier
+Master3 <- Master3 %>%
+    mutate(Spending_Per_Soldier = (usmilex/usmilper))
 
@@
 
-Master4 <- select(Master3, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid, Ally)
+Master3 <- Master3 %>%
+  rename(
+    US_Tonnage = ustoton
+  )
+
+Master4 <- select(Master3, ccodea, ccodeb, year, Mid, Use_Force, Hostility, US_Naval_Cap, Same_Region, Contiguous, Joint_Dem, Relative_Cap, Major, Post_Cold_War, Lag_Mid, Ally, US_Tonnage, Spending_Per_Soldier)
 summary(Master4)
@@
 ODDS_BI_MID <- exp(coef(MID_BI_Log))
-dwplot(MID_BI_Log)
+
+MID2_BI_Log <- glm(Mid ~ US_Tonnage, data = Master4, family=binomial)
+summary(MID2_BI_Log)
+ODDS_BI_MID2 <- exp(coef(MID2_BI_Log))
 
@@
 ODDS_BI_FORCE <- exp(coef(Force_BI_Log))
-dwplot(Force_BI_Log)
+
+Force2_BI_Log <- glm(Use_Force ~ US_Tonnage, data = Master4, family=binomial)
+summary(Force2_BI_Log)
+ODDS_BI_FORCE2 <- exp(coef(Force2_BI_Log))
 
 ```
+
+##Introduction
+
+When Xerxes sought in invade the Greek peninsula, he used several hundred ships lined side by side with wooden planks running between creating a bridge to cross his armies over the Hellespont.
+Despite using his own vessels to build this massive bridge, he still had nearly a thousand warships with which to threaten the Greek coast.
+The war between Athens and Sparta decades later for domination of Greece began partly as a result of the buildup of Athenian naval power and threat of Athenian control over the Greek trade routes.
+In the age of sail the most dominant colonial powers were those with the greatest navies allowing them to protect trade routes and spread their empire through overseas colonization.
+In the Second World War the British and American navies protected the vital convoys which supplied the British and prevented the final bastion of European resistance from falling to the German war machine.
+Naval power has been the backbone of every great empire from antiquity to modernity.
+No major power can become a global power if they are not dominant in terms of naval capabilities.
+But can the powerful fleets of a world power affect the conflicts the occur between the lesser powers in the international system?
+The various schools of international relations theory argue that a hegemon will punish actors who attempt to upset the status quo.
+If a state believes that the hegemon will respond to aggression, does the ability of the hegemon to project power overseas influence the conflictual behavior and decision making of that state?
+This paper will investigate this question and explore any relationships between a hegemon’s naval capability and the conflict behavior of other states in the international system.
+Using several models of logistic regression, this paper will analyze the relationship between militarized interstate dispute onset and severity and the naval capabilities of a hegemonic power.
+The following sections will consist of a review of the prevailing literature on hegemony and conflict initiation as well as the operationalization and effect of naval capabilities.
+I will introduce the theory and the data and methods used in this paper in further detail in the section following that literature review.
+An analysis of the results and a discussion of the implications of this research will conclude the paper.
+
+##Review of Literature
+
+The universe is held together by the gravitational pull of the objects of which it is composed.
+The greater the mass of the object, the greater the gravitational pull.
+Those objects which have the greatest mass will become the centers of their own gravitational systems such as stars becoming the center of solar systems, drawing in planets and asteroids into orbit with its gravity.
+The simple rule of gravity is, the greater the size, the greater the pull.
+Much in the same way that stars and planets are able to capture and dictate the system that surrounds them, so too can powerful states dictate the physics of system in which they reside.
+
+The gravitational pull in this case is the power of the state.
+The most powerful states in the international system can establish rules and order in the international system as they see fit and punish or reward adherence to that order.
+The most powerful of these states is commonly refered to the hegemon.
+The concept of power in international relations is at best vague and open to interpretation.
+However, despite its ambiguity it has been the foundation of international relations research and theory.
+A full examination of the lexicon of the literature which seeks to define power is beyond the scope of this paper.
+For my purposes I observe power in the same way as A.F.K.
+Organski (1968), the ability of a state to change the behavior of another.
+We can observe this ability by measuring the determinants of power; the resources and material capabilities which allow states to interact and influence each other.
+In this research a specific aspect of the international power of states and the hegemon, naval capability, will be the focus.
+
+The concept of a hegemon dates back to the ancient Greeks and the word hēgemonía, which loosely translated means leadership (Smith, 2012).
+According to several schools of international relations theory, the hegemon will establish order in the international system and will endeavor to keep the order.
+George Modelski (1978) referred to the hegemon as the world power and argued that these states were those entities which had a monopoly on “order-keeping” of the world system.
+It was the task of the world power to manage the interdependence of the other units in the international system.
+What provided these world powers the ability to do so, according to Modelski, was their overwhelming advantage in naval capabilities.
+States which have been traditionally seen as being hegemonic powers such as the United States, Great Britain, Spain, and the Netherlands each had enormous preponderance in naval capabilities.
+Great Britain for example in the late 1800s possessed roughly half of all shipping tonnage in the world, along with military ports in colonies worldwide.
+(Calder 2008, 7).
+All five the “cycles” in Modelski’s long cycle theory of international politics featured a single world power with an overwhelming preponderance of naval power (Modelski 1978).
+
+However, there are theorists like John Mearsheimer who argue that naval power has little to do with the establishment or maintenance of a hegemonic order.
+According to his theory which he calls offensive realism, it is land armies which conquer and hold territory and are thus the more important determinant of power (Mearsheimer 2001).
+He even goes as far as to argue that no state can achieve hegemony due to the great stopping power of the world oceans.
+Navies, in the eyes of Mearsheimer, are force multipliers for the land forces and should be considered as supporting the army, not as a potential independent tool for preventing or resolving conflict.
+
+The explanatory variable in this research is the naval capabilities of the prevailing hegemon.
+A large and effective navy can protect shipping lanes, defend strategic coastlines, and allow for the landing of troops and supplies to a territory beyond the reach of the hegemon by land (Corbet 1984; Mahan 2004; Mearsheimer 2001).
+Naval forces have evolved over time with new technologies and changing tactics, but much of the strategy and purpose of naval forces have remained the same.
+States with powerful navies such as the United States and Great Britain in the past, will use their naval power to protect their interests.
+This includes preventing foreign powers from establishing what some refer to as “command of the sea” (Corbett 1984).
+One of the seminal works on the importance of naval power comes from Alfred Mahan.
+Mahan (2004) argued that naval dominance was necessary for states to assume command of the seas, thereby ensuring the success of land operations, cutting off lines of communication and commerce to an enemy, and protecting one’s own commerce and interests.
+Naval forces positioned in strategic locations like Gibraltar or the Suez can allow states to set up blockades and chokepoints, denying an enemy access to the sea and cutting off commerce.
+(Crowl 1986).
+The two most common ways in which to measure naval power is by looking at the number of capital ships a state maintains and by observing the total tonnage of all blue-water capable ships in the states inventory.
+I will review each method in the next few sections.
+
+Not all naval forces are alike.
+States will design their naval forces based on the nature of the mission objectives as well as the area in which those forces will operate.
+A state which uses its navy to protect its coastline and exclusive economic zone will use ships designed for green-water warfare, specializing in littoral operations in shallow waters and mine clearing.
+States which seek to project power a great distance and engage the navies of other states will design their naval forces for blue-water operations and long-range missions.
+The backbone of any naval force is the warship, the vessel which engages in combat with opposing fleets or non-state actors such as pirates.
+Capital ships are often the largest and most heavily armed warships of any fleet and are capable of traveling the greatest distance.
+A single capital ship can destroy entire squadrons of smaller vessels and devastate a coastline.
+During the Second World War, the German battleships Bismarck and Tirpitz were designed to single handedly attack entire allied shipping convoys.
+In the Pacific theater the naval conflict centered around the battleship and carrier forces of the American and Imperial navies.
+The primary targets of the Japanese forces during the attack on Pearl Harbor were the American carriers and battleships tied up in the harbor.
+George Modelski uses capitol ships in his study of naval power and long cycles in international politics (Modelski 1987; Modelski, Thompson 1988).
+
+Sean Bolks and Richard Stoll (2000) also use the number of capital ships in their study of the temporal dynamics of arms races as a measure of naval power.
+They chose this measure over the far more common method of observing the state’s military spending because it offered several benefits.
+First, it avoids some of the greatest problems associated with using military expenditure, differences in the definition and rates of military expenditures in different states.
+The authors use the examples of conscripts, volunteers, and retirees.
+Some states have militaries which rely heavily on conscription as opposed to volunteers.
+This allows them to pay significantly less for a military of the same size as a state which pays for volunteers.
+There is also issues with what exactly is considered part of military expenditures.
+Some countries include pensions for retirees and healthcare for their veterans as military expenditures, causing a balloon in their spending while not contributing to their forces size or capability.
+Other countries have even provided massive subsidies to their domestic military industries resulting in additional massive hikes in their annual military spending without any contribution to force size or composition.
+Bolks and Stoll avoid this issue by focusing only on those ships which are active and contribute to the military power of the state (2000).
+
+An obvious question that arises here is what constitutes a capital ship.
+During what is commonly referred to as the age of sail, a capital ship would have been a ship of the line.
+These large sail powered vessels were armed with multiple rows of cannon which could deliver powerful broadsides.
+A large ship of the line such as the Spanish Santisima Trinidad carried more than 140 cannons; as many as entire land armies.
+The successors of these ships would have been the powerful iron-clads and battleships which dominated the oceans of the late 19th and early 20th centuries (Keegan 1993).
+However, during the interwar period states began experimenting with new technologies which gave rise to new classes of warships.
+The aircraft carrier allowed a fleet to project offensive force hundreds of miles beyond the rand of the big gun battleships, and submarines allowed for stealthy operations below the surface.
+By the end of the war the powerful battlewagons which had ruled the waves for decades had been rendered obsolete.
+Today the criteria for a capital ship is as ambiguous as ever.
+No battleships remain in service anywhere in the world.
+Carriers and nuclear submarines are seen as the hallmarks of an advanced navy and some classes of destroyers today weigh as much as World War 1 battleships.
+Bolks and Stoll (2000) use the number of capital ships recorded in the data compiled by Modelski and Thompson (1988) in their study of global naval power.
+Modelski and Thompson observed that what constitutes a capital ship changes over the years, as described above.
+Thus, they change their operationalization of a capital ship in their own dataset to account for the changes in technology and definition.
+
+Aside from the type of ship, one of the most common ways to measure the capabilities of a fleet is by looking at the total tonnage of every ship in a states inventory.
+Larger ocean-going vessels and the modern equivalent of the capital ships are incredibly heavy machines.
+A larger vessel is able to carry more weapons, armor, and aircraft than a smaller ship making it a more dangerous weapon.
+It was for this reason that states have sought to limit the size of warships in the past.
+The treaties of the Washington Naval Conference of 1921 and the London Naval Conference treaties of 1930 attempted to limit the size of warships by making states agree not to build ships of certain types to exceed a specified tonnage (Gray 2007; McBride 1997).
+Joseph Maiolo (2008) examined the history of British and Soviet relative naval capabilities from the interwar period to the years just before the outbreak of World War 2 by examining the total tonnage of naval shipping produced by both countries.
+William Walters (2000) examined the history of American naval shipbuilding and capability in his historical review of U.S.
+naval ship building.
+Some have used both the measures of total tonnage and the total count of ocean-going ships in measuring naval capabilities.
+(Wolters 2011)
+
+The number of capital ships and the total tonnage of naval inventory are the two most common methods of measuring naval capability.
+However, these measures do not capture one vital concept of capability, the technological quality and efficiency of a navy.
+At the battle of Lepanto (1571) the combined European powers making up the Holy League faced the fleet of the Ottoman Empire.
+Both fleets contained roughly the same number of ships and the same type, roughly 200 galleys using oars and sails.
+The Europeans however also had six new galleasses which were the precursors to the large mast ships of the age-of-sail and were heavily armed for their time.
+These new ship types were extremely effective against the older style galleys and turned the tide in favor of the European coalition (Keegan 1993).
+More recent examples of the importance of technological capability were the submarine races of the Cold War.
+Both the Soviet Union and the United States sought to make their submarines stealthier and more destructive by making them nuclear powered and giving them the ability to launch missiles from underwater.
+China today has more submarines in their fleet than the United States.
+However, most of these ships are older diesel-powered models with a limited range.
+The advanced nuclear-powered submarines used by the United States are quitter, faster, and far more advanced.
+This shortcoming of tonnage and ship counts as measures of naval power was recognized at the Washington Naval Conference by the United States which felt it was getting cheated.
+Woodrow Wilson ordered an engineer to develop what he called a technical yardstick to identify the qualitative differences between ships.
+However, this yardstick was rejected by the other members of the conference and the terms of the treaty called for reductions in tonnage.
+A key question in this research is how to incorporate a measure of technological advancement into the measure of naval capability (McBride 1997).
+
+##Theory
+In this paper I make several assumptions about the international system as well as the actors who occupy it.
+First, unlike John Mearsheimer I assume that states are able to achieve a level of global hegemon, and they are able to so thanks to an overwhelming advantage in naval capabilities.
+Naval power allows a state to control the international shipping lanes, land troops on foreign shores, and protect supply routes from across the sea thus allowing invasion forces to remain supplied and reinforced.
+A state cannot become a hegemon without naval supremacy,
+
+##Method
+	To test my hypothesis that increases in the naval capabilities of a hegemonic power can reduce the propensity of states to engage in militarized disputes or violent militarized disputes, I use the time-tested method of logistic regression.
+This test observes and records the effects of the independent variables and controls on a binary dependent variable.
+One of the benefits of logistic regression is that we can get the odds ratio of a particular outcome occurring, allowing us to conclude how much more likely the event is to occur based on increases in the independent variables.
+Two dependent variables will be tested in this paper, the first being the occurrence of a MID in a given dyad-year.
+The second is the occurrence of a violent MID in a given dyad year defined asa MID which has achieved a hostility level of “use of force” or “war.” Bivariate logistic models will be tested looking only at the dependent and independent variables.
+This will be followed by larger models which will include a series of state and dyad level controls.
+These models will also be replicated using the more traditional measurement of total tonnage of the U.S.
+fleet as a robustness check.
+
+##Data
+The data for this project is drawn from several sources.
+Data on militarized disputes is drawn from the Militarized Interstate Dispute (MIDs) dataset produced by the correlates of war project.
+This data includes information of militarized disputes dating as far back as the early 1800s and as recently as 2012.
+The data includes the start and end dates of the dispute, which state was involved in the dispute coded by both country code and country abbreviation, and who the initiator of the dispute was at the time it started.
+Also included in this dataset is a variable which identifies the highest level of hostility achieved in this dispute.
+This is a catagorical variable with observations for threats of using force, displays of force, use of force, or interstate war.
+An example of threat to use force against an opponent would be former President George W.
+Bushes televised ultimatum to Saddam Hussein where he offered the former Iraqi leader an amount of time to abdicate his power, or else the US would remove him by force.
+Displays of force can include the deploying of troops to a contested region such as the recent deployment of the aircraft carrier USS Abraham Lincoln to the Persian Gulf, or the sailing of U.S.
+warships through the Taiwan Strait.
+The use of force would be any action in which military forces are used to attack a specified target, but the two countries are not yet at a level of open warfare.
+The U.S.
+missile strikes on Syrian airfields or the Israeli bombing of the Iraqi powerplant would constitute a use of force short of open warfare.
+The highest level of hostility is the case of interstate war such as the World Wars.
+This variable will be used and modified in this research into two separate deponent variables which are discussed in more detail below.
+
+Data on the regime type of each member of the dyad was drawn from the PolityIV dataset produced by the Center for Systemic Peace.
+This dataset looks into the domestic political institutions of a state and categorizes that state as being democratic or authoritarian on a scale of -10 to 10.
+There are multiple different datasets which operationalize and measure the level of democracy of a state, the decision to use PolityIV was made based on overwhelming prevalence in international relations literature.
+
+The National Material Capabilities dataset produced by the Correlates of War project was used to get data on the annual material capabilities of each member of the dyad.
+Like most datasets for the COW project, the NMC dataset includes data on every state dating backing to the early 1800s.
+This information includes the year the data was recorded as well as several measures of raw materials and national resources which will be discussed later in this paper when the controls are introduced.
+The data on alliances was also compile by the Correlates of War project and was recorded in the Alliances dataset.
+
+Lastly, data on the naval capabilities of the United States was taken from the Power at Sea dataset compiled by Brian Crisher and Mark Souva of the University of West Florida.
+This data includes observations for the size of state navies for 196 countries from 1865-2011 including the total tonnage of a state’s fleet, the total number of ocean-going vessels, and the proportion of systemic tonnage held by a country in a given year.
+This data will be used to create a new measurement for naval capabilities which accounts for a level of quality in the state’s military.
+
+##Variables
+There are two dependent variables that are tested in this paper, the occurrence of a MID in a dyad year and the occurrence of a MID which involved either the use of force or resulted in an interstate war.
+Both variables are binary and
+
+The independent variable of interest in this paper is the naval capacity of the hegemon.
+The traditional way for researchers to measure naval capacity has been to use either the total tonnage of the ship, or the number of ships in the state’s fleet.
+This is problematic as this does not actually capture the capability of a state’s fleet.
+The best way to illustrate this is with an example.
+Peru currently has within its fleet a De Zeven class cruiser called the Almirante Grau that was built in the Netherlands in 1939 and weighs 9,600 tons.
+If we compare this to an American equivalent the problem becomes painfully clear.
+The American Ticonderoga class cruiser was built in the 1980s and 1990s and weighs almost the exact same, roughly 9,600 tons.
+Two ocean going ships, both catalogued as cruisers, and both weighing roughly 9,600 tons.
+However, one is built using pre-World War 2 technology and can only attack a target that the crew can physically see.
+The American ship on the other hand is armed with more than one-hundred missiles capable of traveling several hundred miles, carries the same radar and tracking system as the U.S.
+ballistic missile shield, and can deploy nuclear weapons.
+There simply is no comparison between these two ships.
+However, in previous literature which only uses either the tonnage or the number or class of ships deployed, these two vessels would be considered the exact same.
+Looking at the data for U.S.
+naval tonnage from 1950-2011, we can see that the amount of tonnage has gone down.
+
+```{r tonnage_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:Tonnage per year"}
+plot(Master4$year, Master4$US_Tonnage, main="US Tonnage Over time",
+    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master4$year,Master4$US_Naval_Cap), col="blue"))
+```
+
+However, as President Barrack Obama once said in a 2012 debate responding to criticism that the U.S.
+fleet has shrunk, “we also have fewer horses and bayonets.” The former President is alluding to the fact that despite the size of the fleet shrinking, the capability of the U.S.
+Navy has increased.
+There is clearly a need to measure what can best be described as the quality of the fleet in order to gain real insight into the capability of the fleet.
+
+In creating a new measure of naval capability I decided to focus on the capital intensity of the state and the investment into its naval forces.
+Using the national material capabilities data, I produced what I very broadly called a quality variable by taking the total military expenditures for the US by year and divided that by the number of military personnel.
+This gave me a variable that measured the amount spend per capita of the U.S.
+military.
+
+```{r Spending_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:Spending per capita"}
+plot(Master4$year, Master4$Spending_Per_Soldier, main="Spending per soldier",
+    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master4$year,Master4$US_Naval_Cap), col="blue"))
+```
+
+I then multiplied this by the proportion tonnage of the entire international system that had been capture by the U.S.
+in that year.
+This gives me a new naval capability variable which shows a steady and monotonic rise from 1950 to 2011, coinciding the large increase in the amount spend by the U.S.
+military per soldier that occurred after the end of the Cold War.
+
+```{r Naval_Capabilities_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:Bivariate_Naval_Cap"}
+plot(Master4$year, Master4$US_Naval_Cap, main="US Naval Capabilities Over Time",
+    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Master4$year,Master4$US_Naval_Cap), col="blue"))
+    ```
+
+The controls for this research are chosen as some of the more common control measures in international conflict research.
+They control for alternative explanations associated with the regime type of the combatants, the relative strength of one combatant to the other, geographic proximity, and alliance structure.
+
+The relative capability of the two actors as measured using taking the CINC scores of the first actor in the dyad divided by the second actor.
+CINC scores are a composite measure of the material capabilities of the state and is produced as part of the National Material Capabilities data by the Correlates of War Project.
+The index is creating by factoring in roughly a half dozen different annual variables including military personnel, military expenditure, urban population, total population, iron and steel production and energy consumption.
+
+A variable identifying if the members of the dyad are in the same region is also included as well as a variable identifying what degree of contiguity the members of the dyad share.
+Geographic proximity and contiguity have been theorized to make conflict more likely as the members of the dyad are physically closer and have more access to the other member.
+Another control is added to account for the impact of regime type and the democratic peace.
+Polity identifies a country as being a democracy if its polity score is greater than 6.
+If both of the members of the dyad have polity scores above a 6, then the dyad is jointly democratic.
+
+A variable identifying if at least one member of the dyad is a major power is included in the model as major powers will have greater capabilities and a possible interest in initiating a conflict.
+A major power may seek to punish another state if that state is trying to disturb the status quo or jeopardize upon the major power’s interests.
+Similarly, if the other state is a rising country trying to become a regional power, then a major power may attempt to stymie their rise.
+
+The last variable included in this dataset is one which identifies if the members of the dyad have an alliance.
+The specific type of alliance is not observed in this project, but rather the existance of one.
+Using the alliance data compiled by the Correlates of War project, a variable was created identifying if a defensive alliance, nonaggression pact, neutrality agreement, or and entente existed between the member of the dyad.
+If one of these alliances existed, then the variable was coded as being “on.” If no alliance was present, then the variable was coded as being “off.”
+
+##Analysis
+
+The plot of the first set of results shows the
+
+```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}
+
+dwplot(list(MID_BI_Log, Force_BI_Log),
+        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))
+
+```
+
+The results of the bivariate test on violent MID ocurence
+
+```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}
+
+dwplot(list(MID_BI_Log, Force_BI_Log),
+        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))
+
+```
+
+##Conclusion
+In this paper I have sought to form a more complete measurement for the naval capability of a hegemonic power that went beyond the traditional measurements of fleet size.
+By factoring in the level of capital intensity per capita of the state in its military I have created a measure which incorporates the traditional measurement for systemic tonnage as well as taking into consideration the quality of the state’s military.
+The result was a variable which demonstrated a monotonic increase in naval capabilities from the early 1950s to the present day.
+This stands in contrast to the traditional measurement of total naval tonnage which demonstrated a near monotonic decrease across the same time period, despite substantial improvements in the quality of the fleet.
+After creating my new variables and running my statistical tests, I have found evidence to support both of my hypotheses.
+The logistic regressions demonstrate that there is a statistically significant negative relationship between the naval capability of the hegemon and the propensity for dyads to experience a militarized dispute.
+This research has plenty of room for improvement in future iterations.
+First, this paper has only examined the impact of naval capabilities during the time of a single historic hegemon.
+Future research may include observations for the naval capabilities of past super powers such as the United Kingdom, Spain, and the Netherlands, three hegemonic powers which possessed substantial naval capabilities.
+New and improved measurements for naval capabilities as more data becomes available as well as the inclusion of additional control parameters are sure to be tested as well.

### 2019-05-11 Paper_markdown.Rmd
Working

@@
 
+#Full Models
+  #Logistic regression
+MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
+summary(MID_Full_Log) 
+dwplot(MID_Full_Log)
+
+MID_Full_Log <- glm(Mid ~ US_Tonnage + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
+summary(MID_Full_Log)
+
+ODDS_MID_FULL <- exp(coef(MID_Full_Log))
+dwplot(ODDS_MID_FULL, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
+
+cplot(MID_Full_Log, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")
+
+Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master4, family=binomial)
+ODDS_FORCE_FULL <- exp(coef(Force_Full_Log))
+dwplot(ODDS_FORCE_FULL, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
+
+Test <- with(Mid, data.frame(US_Naval_Cap = 0:19, Relative_Cap=mean(Relative_Cap, na.rm=TRUE), Joint_Dem=mean(Joint_Dem, na.rm=TRUE), Major=mean(Major, na.rm=TRUE), Same_Region=mean(Same_Region, na.rm=TRUE), Contiguous=mean(Contiguous, na.rm=TRUE), Ally=mean(Ally, na.rm=TRUE)))
+
+Pred_MID_LOG <- predict(m, Test, type="response", se.fit=TRUE)
+
+margins(MID_Full_Log, at = list(US_Naval_Cap = 0:19))
+cplot(MID_Full_Log, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")
+
+Force_Full_Log2 <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid + Ally, data = Master4, family=binomial)
+summary(Force_Full_Log2)
+dwplot(Force_Full_Log2, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
+exp(coef(Force_Full_Log2))
+test1 <- data.frame(exp(coef(Force_Full_Log2)))
+ggplot(exp(coef(Force_Full_Log2)))
+
+margins(Force_Full_Log2)
+cplot(Force_Full_Log2, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of (violent)MID given US naval capabilities")
+
+MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War, data = Master4, family=binomial)
+summary(MID_Full_Log)
+dwplot(MID_Full_Log)
+
+Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
+summary(Force_Full_Log)
+dwplot(Force_Full_Log)
+
 ```
@@
 ##Analysis
-
 The plot of the first set of results shows the
 
-```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}
+```{r dotwhisker_bivariate_mid, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}
 
-dwplot(list(MID_BI_Log, Force_BI_Log),
-        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))
-
+dwplot(list(MID_BI_Log, MID2_BI_Log),
+        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) + ggtitle("test")
 ```
@@
 
-```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}
+```{r dotwhisker_bivariate_force, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on violent MID occurence"}
 
-dwplot(list(MID_BI_Log, Force_BI_Log),
+dwplot(list(Force_BI_Log, Force2_BI_Log),
         vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))
+```
 
-```
+Looking
+
+```{r dotwhisker_bivariate_force, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Full tests on MID occurence"}
+dwplot(ODDS_MID_FULL, show_intercept=TRUE, vline=geom_vline(xintercept=0), dot_args = list(size=3))
 

### 2019-05-11 Paper_markdown.Rmd
I beleive i finally have the errors fixed, and can finally commit.

--- 2019-05-11 Paper_markdown.Rmd
@@
   affiliation: University of Iowa
-abstract: "Here's where you write 100 to 250 words, depending on the journal, that describe your objective, methods, results, and conclusion."
+abstract: "Research which has examined the effects of naval capabilities on conflict behavior have done so by examining different measures for the size of a state's navy.
+However, this does not capture the actualy capabilities of a country's fleet.
+In this article I create a new measurement for naval capability and use it to test the effect of a hegemon's naval power on the conflict behavior of other states in the international system.
+I find that higher levels of naval power held by the hegemon reduces the liklihood that a militarized dispute will occur."
 keywords: "Naval power hegemony"
@@
 spacing: single
-bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "bib$"))`}
+bibliography: Naval.bib
 biblio-style: apsr
@@
 ```{r, include=FALSE, cache=TRUE}
-
-#Merging datasets
-
 #mergin in dyadic mid data
@@
 Master2 <- merge(Master2, USNaval, by=c("year"), all.x = TRUE)
-
-plot(Naval2$year, Naval2$totton, main="US Naval Capabilities Over Time",
-    xlab = "Year", ylab = "US Naval Capabilities", lines(lowess(Naval2$year,Naval2$totton), col="blue"))
 
@@
 summary(Master4)
+
 ```
@@
 ODDS_BI_FORCE2 <- exp(coef(Force2_BI_Log))
+
+#Full Models
+  #Logistic regression
+MID_Full_Log <- glm(Mid ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
+summary(MID_Full_Log)
+
+cplot(MID_Full_Log, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")
+
+#Full Force model
+Force_Full_Log <- glm(Use_Force ~ US_Naval_Cap + Relative_Cap + Joint_Dem + Major + Same_Region + Contiguous + Ally + Post_Cold_War + Lag_Mid, data = Master4, family=binomial)
+
+cplot(Force_Full_Log, "US_Naval_Cap", what = "prediction", main = "Predicted occurence ofa violent MID given US naval capabilities")
 
@@
 For my purposes I observe power in the same way as A.F.K.
-Organski (1968), the ability of a state to change the behavior of another.
+Organski, the ability of a state to change the behavior of another @Organski1968.
 We can observe this ability by measuring the determinants of power; the resources and material capabilities which allow states to interact and influence each other.
@@
 
-The concept of a hegemon dates back to the ancient Greeks and the word hēgemonía, which loosely translated means leadership (Smith, 2012).
+The concept of a hegemon dates back to the ancient Greeks and the word hēgemonía, which loosely translated means leadership @Smith2012.
 According to several schools of international relations theory, the hegemon will establish order in the international system and will endeavor to keep the order.
@@
 Great Britain for example in the late 1800s possessed roughly half of all shipping tonnage in the world, along with military ports in colonies worldwide.
-(Calder 2008, 7).
-All five the “cycles” in Modelski’s long cycle theory of international politics featured a single world power with an overwhelming preponderance of naval power (Modelski 1978).
+@Calder2007.
+All five the “cycles” in Modelski’s long cycle theory of international politics featured a single world power with an overwhelming preponderance of naval power @Modelski1978.
 
 However, there are theorists like John Mearsheimer who argue that naval power has little to do with the establishment or maintenance of a hegemonic order.
-According to his theory which he calls offensive realism, it is land armies which conquer and hold territory and are thus the more important determinant of power (Mearsheimer 2001).
+According to his theory which he calls offensive realism, it is land armies which conquer and hold territory and are thus the more important determinant of power @Mearsheimer2001.
 He even goes as far as to argue that no state can achieve hegemony due to the great stopping power of the world oceans.
@@
 The explanatory variable in this research is the naval capabilities of the prevailing hegemon.
-A large and effective navy can protect shipping lanes, defend strategic coastlines, and allow for the landing of troops and supplies to a territory beyond the reach of the hegemon by land (Corbet 1984; Mahan 2004; Mearsheimer 2001).
+A large and effective navy can protect shipping lanes, defend strategic coastlines, and allow for the landing of troops and supplies to a territory beyond the reach of the hegemon by land @Corbett1984 @Mahan2004 @Mearsheimer2001.
 Naval forces have evolved over time with new technologies and changing tactics, but much of the strategy and purpose of naval forces have remained the same.
 States with powerful navies such as the United States and Great Britain in the past, will use their naval power to protect their interests.
-This includes preventing foreign powers from establishing what some refer to as “command of the sea” (Corbett 1984).
+This includes preventing foreign powers from establishing what some refer to as “command of the sea” @Corbett1984.
 One of the seminal works on the importance of naval power comes from Alfred Mahan.
-Mahan (2004) argued that naval dominance was necessary for states to assume command of the seas, thereby ensuring the success of land operations, cutting off lines of communication and commerce to an enemy, and protecting one’s own commerce and interests.
+Mahan argued that naval dominance was necessary for states to assume command of the seas, thereby ensuring the success of land operations, cutting off lines of communication and commerce to an enemy, and protecting one’s own commerce and interests @Mahan2004.
 Naval forces positioned in strategic locations like Gibraltar or the Suez can allow states to set up blockades and chokepoints, denying an enemy access to the sea and cutting off commerce.
-(Crowl 1986).
+@Crowl1986.
 The two most common ways in which to measure naval power is by looking at the number of capital ships a state maintains and by observing the total tonnage of all blue-water capable ships in the states inventory.
@@
 The primary targets of the Japanese forces during the attack on Pearl Harbor were the American carriers and battleships tied up in the harbor.
-George Modelski uses capitol ships in his study of naval power and long cycles in international politics (Modelski 1987; Modelski, Thompson 1988).
+George Modelski uses capitol ships in his study of naval power and long cycles in international politics @Modelski1987 Modelski1988.
 
-Sean Bolks and Richard Stoll (2000) also use the number of capital ships in their study of the temporal dynamics of arms races as a measure of naval power.
+Sean Bolks and Richard Stoll also use the number of capital ships in their study of the temporal dynamics of arms races as a measure of naval power @Bolks2000.
 They chose this measure over the far more common method of observing the state’s military spending because it offered several benefits.
@@
 Other countries have even provided massive subsidies to their domestic military industries resulting in additional massive hikes in their annual military spending without any contribution to force size or composition.
-Bolks and Stoll avoid this issue by focusing only on those ships which are active and contribute to the military power of the state (2000).
+Bolks and Stoll avoid this issue by focusing only on those ships which are active and contribute to the military power of the state @Bolks2000.
 
@@
 A large ship of the line such as the Spanish Santisima Trinidad carried more than 140 cannons; as many as entire land armies.
-The successors of these ships would have been the powerful iron-clads and battleships which dominated the oceans of the late 19th and early 20th centuries (Keegan 1993).
+The successors of these ships would have been the powerful iron-clads and battleships which dominated the oceans of the late 19th and early 20th centuries @Keegan1993.
 However, during the interwar period states began experimenting with new technologies which gave rise to new classes of warships.
@@
 Carriers and nuclear submarines are seen as the hallmarks of an advanced navy and some classes of destroyers today weigh as much as World War 1 battleships.
-Bolks and Stoll (2000) use the number of capital ships recorded in the data compiled by Modelski and Thompson (1988) in their study of global naval power.
+Bolks and Stoll use the number of capital ships recorded in the data compiled by Modelski in their study of global naval power @Bolks2000.
 Modelski and Thompson observed that what constitutes a capital ship changes over the years, as described above.
@@
 It was for this reason that states have sought to limit the size of warships in the past.
-The treaties of the Washington Naval Conference of 1921 and the London Naval Conference treaties of 1930 attempted to limit the size of warships by making states agree not to build ships of certain types to exceed a specified tonnage (Gray 2007; McBride 1997).
-Joseph Maiolo (2008) examined the history of British and Soviet relative naval capabilities from the interwar period to the years just before the outbreak of World War 2 by examining the total tonnage of naval shipping produced by both countries.
-William Walters (2000) examined the history of American naval shipbuilding and capability in his historical review of U.S.
-naval ship building.
+The treaties of the Washington Naval Conference of 1921 and the London Naval Conference treaties of 1930 attempted to limit the size of warships by making states agree not to build ships of certain types to exceed a specified tonnage @Gray2007 @McBride1997.
+Joseph Maiolo examined the history of British and Soviet relative naval capabilities from the interwar period to the years just before the outbreak of World War 2 by examining the total tonnage of naval shipping produced by both countries @Maiolo2008.
+William Walters examined the history of American naval shipbuilding and capability in his historical review of U.S.
+naval ship building @Walters2000.
 Some have used both the measures of total tonnage and the total count of ocean-going ships in measuring naval capabilities.
-(Wolters 2011)
+@Wolters2011
 
@@
 The Europeans however also had six new galleasses which were the precursors to the large mast ships of the age-of-sail and were heavily armed for their time.
-These new ship types were extremely effective against the older style galleys and turned the tide in favor of the European coalition (Keegan 1993).
+These new ship types were extremely effective against the older style galleys and turned the tide in favor of the European coalition @Keegan1993.
 More recent examples of the importance of technological capability were the submarine races of the Cold War.
@@
 However, this yardstick was rejected by the other members of the conference and the terms of the treaty called for reductions in tonnage.
-A key question in this research is how to incorporate a measure of technological advancement into the measure of naval capability (McBride 1997).
+A key question in this research is how to incorporate a measure of technological advancement into the measure of naval capability McBride1997.
 
@@
 	In this paper I make several assumptions about the international system as well as the actors who occupy it.
-First, unlike John Mearsheimer I assume that states are able to achieve a level of global hegemon, and they are able to so thanks to an overwhelming advantage in naval capabilities.
+First, unlike John Mearsheimer I assume that states are able to become a global hegemon, and they are able to do so thanks to an overwhelming advantage in naval capabilities.
 Naval power allows a state to control the international shipping lanes, land troops on foreign shores, and protect supply routes from across the sea thus allowing invasion forces to remain supplied and reinforced.
-A state cannot become a hegemon without naval supremacy,
+Without a powerful navy, no state can become a hegemon, but this does not mean that a state cannot gain the naval capabilities necessary to create and enforce and international order.
+	Other states in the international system will understand that the hegemon has an interest in maintaining the status quo and that the hegemon will punish those who try to upset the international order.
+With this in mind, states will be less inclined to engage in conflictual behavior and risk the hegemon responding.
+Unless that state shares a land border with the hegemon, thill will mean that the state will be wary of the hegemon’s naval capabilities as it will be their navy that allows them to respond to any action in the international system.
+In this paper I present two simple hypotheses:
+H1) Greater naval capability by the hegemon will result in a lower propensity for a dyad to experience a MID in a given year.
+H2) Greater naval capability by the hegemon will result in a lower propensity for a dyad to experience a MID which involves the use of force in a given year.
+I expect the results of my statistical test to show a statistically significant negative relationship between the hegemon’s naval capabilities and the likelihood of a MID occurring.
+Additionally, I expect that each of the additional controls I am including will be statistically significant, as each of them have been found to be so in different studies.
 
@@
 ##Analysis
+Figure four gives the unstandardized coefficents of the bivariate test of my independant and dependant variables.
+Total US tonnage, the traditional measure used by a vast majority of the naval capabilities literature, appears to demonstrate a positive relationship on the occurence of a militaized dispute.
+However, the measure for naval capabilities which takes into account the quality of fleet shows a statistically significant negative relationship.
 
-The plot of the first set of results shows the
+```{r dotwhisker_bivariate_mid, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}
 
-```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}
-
-dwplot(list(MID_BI_Log, Force_BI_Log),
-        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))
-
+dwplot(list(MID_BI_Log, MID2_BI_Log),
+        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) + ggtitle("Bivariate test of the occurence of MIDs")
 ```
 
-The results of the bivariate test on violent MID ocurence
+The results of the bivariate test on violent MID ocurence displayed in figure 5 shows an almost completely identicle result with total US tonnage demonstrateing positive relationship with weak statistical significance towards the occurrence of a MID which involved the use of force.
+However, the naval capability measure agains shows a negative relationship with viovlent MID occurrence and has strong statistical signficance.
 
-```{r dotwhisker_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on MID occurence"}
+```{r dotwhisker_full_Mid, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Bivariate tests on violent MID occurence"}
 
-dwplot(list(MID_BI_Log, Force_BI_Log),
-        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2))
+dwplot(list(MID_BI_Log, MID2_BI_Log),
+        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) + ggtitle("Bivariate test of the occurence of the use of force")
+```
+
+Figure 6 gives us the full models of the occurrence of a MID and the occurrence of a MID with the use of force.
+Each variable is statistically significant at the 0.5 level with both models displaying very similar results.
+Model one tests the occurrence of a MID with the new naval capabilities measure while model 2 tests the occurrence of a violent MID with the full model.
+In both models higher levels of US naval capability see a statistically significant negative relationship with the occurrence of a MID and the occurence of a MID involving somekind of use of force.
+
+```{r dotwhisker_bivariate_force, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Full tests on MID occurence"}
+dwplot(list(MID_Full_Log, Force_Full_Log),
+        vline = geom_vline(xintercept = 0, colour = "grey60", linetype = 2)) + ggtitle("Full model of MID occurrence and the use of force")
+```
+
+This effect is even more clear when looking at the marginal effects plots of figure 7 and figure 8.
+The marginal effects of both models show us that as the U.S.
+level of naval capailbity increases, the likelihood of a MID or a violent MID occuring drops dramatically.
+
+```{r Marginal_MID, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Marginal effects of MID occurrence"}
+
+cplot(MID_Full_Log, "US_Naval_Cap", what = "prediction", main = "Predicted occurence of MID given US naval capabilities")
+```
+
+```{r Marginal_Force, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="Marginal effects of violent MID occurrence"}
+
+cplot(Force_Full_Log, "US_Naval_Cap", what = "prediction", main = "Predicted occurence ofa violent MID given US naval capabilities")
 

### 2019-05-13 Paper_markdown.Rmd
fix paths to datasets and .bib file; omit calls to `View()`; fix headings

@@
 spacing: single
-bibliography: Naval.bib
+bibliography: \dummy{`r file.path(getwd(), list.files(getwd(), "Naval\\.bib$"))`}
 biblio-style: apsr
@@
 
-dyadic_mid_3_1_may_2018 <- as.data.frame( read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/dyadic_mid_3.1_may_2018.dta"))
-View(dyadic_mid_3_1_may_2018)
+dyadic_mid_3_1_may_2018 <- read_dta("Data/dyadic_mid_3.1_may_2018.dta")
 
@@
 #Relative capabilities data
-NMC_5_0 <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/NMC_5_0.dta"))
-View(NMC_5_0)
+NMC_5_0 <- read_dta("Data/NMC_5_0.dta")
 NMC <- select(NMC_5_0, ccode, year, irst, milex, milper, pec, tpop, upop, cinc)
@@
 #Importing naval data, removing all but the data for the U.S., keeping only relevant variables.
-crisher_souva_navaldata_II <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/crisher_souva_navaldata_II.dta"))
+crisher_souva_navaldata_II <- read_dta("Data/crisher_souva_navaldata_II.dta")
 Naval1 <- filter(crisher_souva_navaldata_II, cowcode == 2)
@@
   )
-view(USNaval)
 
 #Importing PolityIV data and creating two seperate datasets to apply to both members of the dyad.
-PolityIV <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/PolityIV.dta"))
+PolityIV <- read_dta("Data/PolityIV.dta")
 
@@
   )
-view(PolityIVa)
 
@@
 
-Alliance <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/alliance_v4.1_by_directed_yearly.dta"))
+Alliance <- read_dta("Data/alliance_v4.1_by_directed_yearly.dta")
 Alliance <- Alliance %>%
@@
 
-politically_relevant <- as.data.frame(read_dta("C:/Users/packe/Documents/Methods_3/Paper/Datasets/politically_relevant.dta"))
+politically_relevant <- read_dta("Data/politically_relevant.dta")
 view(politically_relevant)
@@
 
-##Introduction
+## Introduction
 
@@
 
-##Review of Literature
+## Review of Literature
 
@@
 
-##Theory
+## Theory
 	In this paper I make several assumptions about the international system as well as the actors who occupy it.
@@
 
-##Method
+## Method
 	To test my hypothesis that increases in the naval capabilities of a hegemonic power can reduce the propensity of states to engage in militarized disputes or violent militarized disputes, I use the time-tested method of logistic regression.
@@
 
-##Data
+## Data
 The data for this project is drawn from several sources.
@@
 
-##Variables
+## Variables
 There are two dependent variables that are tested in this paper, the occurrence of a MID in a dyad year and the occurrence of a MID which involved either the use of force or resulted in an interstate war.
@@
 
-##Analysis
+## Analysis
 Figure four gives the unstandardized coefficents of the bivariate test of my independant and dependant variables.
@@
 
-##Conclusion
+## Conclusion
 In this paper I have sought to form a more complete measurement for the naval capability of a hegemonic power that went beyond the traditional measurements of fleet size.

### 2019-05-15 Paper_markdown.Rmd
use parenthetical citations; fix figure labels

@@
 
-When Xerxes sought in invade the Greek peninsula, he used several hundred ships lined side by side with wooden planks running between creating a bridge to cross his armies over the Hellespont.
+When Xerxes sought to invade the Greek peninsula, he used several hundred ships lined side by side with wooden planks running between creating a bridge to cross his armies over the Hellespont.
 Despite using his own vessels to build this massive bridge, he still had nearly a thousand warships with which to threaten the Greek coast.
@@
 For my purposes I observe power in the same way as A.F.K.
-Organski, the ability of a state to change the behavior of another @Organski1968.
+Organski, the ability of a state to change the behavior of another [@Organski1968].
 We can observe this ability by measuring the determinants of power; the resources and material capabilities which allow states to interact and influence each other.
@@
 
-The concept of a hegemon dates back to the ancient Greeks and the word hēgemonía, which loosely translated means leadership @Smith2012.
+The concept of a hegemon dates back to the ancient Greeks and the word hēgemonía, which loosely translated means leadership [@Smith2012].
 According to several schools of international relations theory, the hegemon will establish order in the international system and will endeavor to keep the order.
@@
 States which have been traditionally seen as being hegemonic powers such as the United States, Great Britain, Spain, and the Netherlands each had enormous preponderance in naval capabilities.
-Great Britain for example in the late 1800s possessed roughly half of all shipping tonnage in the world, along with military ports in colonies worldwide.
-@Calder2007.
-All five the “cycles” in Modelski’s long cycle theory of international politics featured a single world power with an overwhelming preponderance of naval power @Modelski1978.
+Great Britain for example in the late 1800s possessed roughly half of all shipping tonnage in the world, along with military ports in colonies worldwide [@Calder2007].
+All five the “cycles” in Modelski’s long cycle theory of international politics featured a single world power with an overwhelming preponderance of naval power [@Modelski1978].
 
 However, there are theorists like John Mearsheimer who argue that naval power has little to do with the establishment or maintenance of a hegemonic order.
-According to his theory which he calls offensive realism, it is land armies which conquer and hold territory and are thus the more important determinant of power @Mearsheimer2001.
+According to his theory which he calls offensive realism, it is land armies which conquer and hold territory and are thus the more important determinant of power [@Mearsheimer2001].
 He even goes as far as to argue that no state can achieve hegemony due to the great stopping power of the world oceans.
@@
 The explanatory variable in this research is the naval capabilities of the prevailing hegemon.
-A large and effective navy can protect shipping lanes, defend strategic coastlines, and allow for the landing of troops and supplies to a territory beyond the reach of the hegemon by land @Corbett1984 @Mahan2004 @Mearsheimer2001.
+A large and effective navy can protect shipping lanes, defend strategic coastlines, and allow for the landing of troops and supplies to a territory beyond the reach of the hegemon by land [@Corbett1984; @Mahan2004; @Mearsheimer2001].
 Naval forces have evolved over time with new technologies and changing tactics, but much of the strategy and purpose of naval forces have remained the same.
 States with powerful navies such as the United States and Great Britain in the past, will use their naval power to protect their interests.
-This includes preventing foreign powers from establishing what some refer to as “command of the sea” @Corbett1984.
+This includes preventing foreign powers from establishing what some refer to as “command of the sea” [@Corbett1984].
 One of the seminal works on the importance of naval power comes from Alfred Mahan.
-Mahan argued that naval dominance was necessary for states to assume command of the seas, thereby ensuring the success of land operations, cutting off lines of communication and commerce to an enemy, and protecting one’s own commerce and interests @Mahan2004.
+Mahan argued that naval dominance was necessary for states to assume command of the seas, thereby ensuring the success of land operations, cutting off lines of communication and commerce to an enemy, and protecting one’s own commerce and interests [@Mahan2004].
 Naval forces positioned in strategic locations like Gibraltar or the Suez can allow states to set up blockades and chokepoints, denying an enemy access to the sea and cutting off commerce.
-@Crowl1986.
+[@Crowl1986].
 The two most common ways in which to measure naval power is by looking at the number of capital ships a state maintains and by observing the total tonnage of all blue-water capable ships in the states inventory.
@@
 The primary targets of the Japanese forces during the attack on Pearl Harbor were the American carriers and battleships tied up in the harbor.
-George Modelski uses capitol ships in his study of naval power and long cycles in international politics @Modelski1987 Modelski1988.
+George Modelski uses capitol ships in his study of naval power and long cycles in international politics [@Modelski1987; @Modelski1988].
 
-Sean Bolks and Richard Stoll also use the number of capital ships in their study of the temporal dynamics of arms races as a measure of naval power @Bolks2000.
+Sean Bolks and Richard Stoll also use the number of capital ships in their study of the temporal dynamics of arms races as a measure of naval power [@Bolks2000].
 They chose this measure over the far more common method of observing the state’s military spending because it offered several benefits.
@@
 Other countries have even provided massive subsidies to their domestic military industries resulting in additional massive hikes in their annual military spending without any contribution to force size or composition.
-Bolks and Stoll avoid this issue by focusing only on those ships which are active and contribute to the military power of the state @Bolks2000.
+Bolks and Stoll avoid this issue by focusing only on those ships which are active and contribute to the military power of the state [@Bolks2000].
 
@@
 A large ship of the line such as the Spanish Santisima Trinidad carried more than 140 cannons; as many as entire land armies.
-The successors of these ships would have been the powerful iron-clads and battleships which dominated the oceans of the late 19th and early 20th centuries @Keegan1993.
+The successors of these ships would have been the powerful iron-clads and battleships which dominated the oceans of the late 19th and early 20th centuries [@Keegan1993].
 However, during the interwar period states began experimenting with new technologies which gave rise to new classes of warships.
@@
 Carriers and nuclear submarines are seen as the hallmarks of an advanced navy and some classes of destroyers today weigh as much as World War 1 battleships.
-Bolks and Stoll use the number of capital ships recorded in the data compiled by Modelski in their study of global naval power @Bolks2000.
+Bolks and Stoll use the number of capital ships recorded in the data compiled by Modelski in their study of global naval power [@Bolks2000].
 Modelski and Thompson observed that what constitutes a capital ship changes over the years, as described above.
@@
 It was for this reason that states have sought to limit the size of warships in the past.
-The treaties of the Washington Naval Conference of 1921 and the London Naval Conference treaties of 1930 attempted to limit the size of warships by making states agree not to build ships of certain types to exceed a specified tonnage @Gray2007 @McBride1997.
-Joseph Maiolo examined the history of British and Soviet relative naval capabilities from the interwar period to the years just before the outbreak of World War 2 by examining the total tonnage of naval shipping produced by both countries @Maiolo2008.
+The treaties of the Washington Naval Conference of 1921 and the London Naval Conference treaties of 1930 attempted to limit the size of warships by making states agree not to build ships of certain types to exceed a specified tonnage [@Gray2007; @McBride1997].
+Joseph Maiolo examined the history of British and Soviet relative naval capabilities from the interwar period to the years just before the outbreak of World War 2 by examining the total tonnage of naval shipping produced by both countries [@Maiolo2008].
 William Walters examined the history of American naval shipbuilding and capability in his historical review of U.S.
-naval ship building @Walters2000.
-Some have used both the measures of total tonnage and the total count of ocean-going ships in measuring naval capabilities.
-@Wolters2011
+naval ship building [@Walters2000].
+Some have used both the measures of total tonnage and the total count of ocean-going ships in measuring naval capabilities [@Wolters2011].
 
@@
 The Europeans however also had six new galleasses which were the precursors to the large mast ships of the age-of-sail and were heavily armed for their time.
-These new ship types were extremely effective against the older style galleys and turned the tide in favor of the European coalition @Keegan1993.
+These new ship types were extremely effective against the older style galleys and turned the tide in favor of the European coalition [@Keegan1993].
 More recent examples of the importance of technological capability were the submarine races of the Cold War.
@@
 Without a powerful navy, no state can become a hegemon, but this does not mean that a state cannot gain the naval capabilities necessary to create and enforce and international order.
+
 Other states in the international system will understand that the hegemon has an interest in maintaining the status quo and that the hegemon will punish those who try to upset the international order.
@@
 In this paper I present two simple hypotheses:
+
 H1) Greater naval capability by the hegemon will result in a lower propensity for a dyad to experience a MID in a given year.
+
 H2) Greater naval capability by the hegemon will result in a lower propensity for a dyad to experience a MID which involves the use of force in a given year.
+
 I expect the results of my statistical test to show a statistically significant negative relationship between the hegemon’s naval capabilities and the likelihood of a MID occurring.
@@
 
-```{r tonnage_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:Tonnage per year"}
+```{r tonnage_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:tonnage}Tonnage per year"}
 plot(Master4$year, Master4$US_Tonnage, main="US Tonnage Over time",
@@
 
-```{r Spending_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:Spending per capita"}
+```{r Spending_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:spending}Spending per capita"}
 plot(Master4$year, Master4$Spending_Per_Soldier, main="Spending per soldier",
@@
 
-```{r Naval_Capabilities_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:Bivariate_Naval_Cap"}
+```{r Naval_Capabilities_plot, fig.width = 7, fig.height = 4, warning = FALSE, message = FALSE, echo = FALSE, fig.cap="\\label{fig:capability}Bivariate Naval Capabilities"}
 plot(Master4$year, Master4$US_Naval_Cap, main="US Naval Capabilities Over Time",
